\section{Abstract and Roadmap}

\paragraph{Abstract.}
The classical stability problem asks for a dimension-free constant controlling
row-stochastic almost-idempotent matrices: if the rows of a nonnegative
matrix sum to one and the two-step transition matrix is close to the one-step
transition matrix, must the matrix be close in row \(\ell^1\) norm to an
exact stochastic idempotent?  In the equivalent signed formulation used here,
one studies an exact affine retraction \(P\), meaning \(P\one=\one\) and
\(P^2=P\), whose rows may have small negative coefficient mass.  The parameter
\(\delta\) is the largest row negative mass and \(\tau=\sqrt{\delta}\).

The two-day campaign recorded here did not finish the classical theorem and
did not produce a counterexample.  Its outcome is a compressed residual: the
original open problem is reduced, through audited and conditionally audited
steps, to a geometric localization statement for hidden rows.  The report's
honest headline chain is
\[
  \mathrm{op}\text{-classical}
  \leq
  \mathrm{op}\text{-exposed-hull}
  \leq
  \mathrm{HLC}
  \leq
  \mathrm{DMF}.
\]
Here HLC is the hidden localization claim, the assertion that a hidden row's
height is \(O(\tau)\); DMF is deep-witness mass forcing, the assertion that an
optimal failed-exposedness witness, a dual certificate that a row is not
well-exposed, carries a universal amount of mass at deficit within the
permitted depth window.  \(\openbadge\) The current formulation of the open is
sharper still: after the proved \(\sigtilde\le\tau\) branch, HLC is equivalent,
at the report's level of reduction, to excluding a hidden top vertex with
\(\sigtilde>\tau\) at height \(H>B\tau\) for a universal constant \(B\).  In
words, the remaining problem is signed quantitative Baake--Sumner stability:
the exact \(\delta=0\) Baake--Sumner theorem gives equal-input recurrent
classes for stochastic idempotents, while the missing perturbative statement
must rule out signed shallow hidden webs at height comparable to \(\tau\).

\paragraph{Reader contract.}
This report is meant to be readable with basic linear algebra, convexity, and
finite-state Markov chains.  A row is viewed both as a vector of coefficients
and as a point in an affine row polytope.  A well-exposed row is one separated
from far rows by an affine test function with the fixed scales
\(\rho=4\tau\) and \(\kappa=\tau/4\).  The set of well-exposed rows is
\(\W\), and the hidden height \(H\) is the \(\ell^1\)-distance from the row
polytope to \(\conv(\W)\).  Later sections give the precise definitions; this
section only fixes the reading map and the status of the conclusions.

The symbol \(\sigtilde\) is geometric: it measures positive coefficient mass
on rows outside \(\conv(\W)\), with an \(\varepsilon\)-halo convention when
one needs depth slack.  Rows in that halo are automatically deep for the
canonical separator.  Some late numerical probes measured an index-based proxy
instead; the report distinguishes that proxy from the geometric quantity.
This distinction is one of the main notation corrections after the first
historical wall language was written.

\paragraph{Early nickname glossary.}
The campaign names used later are shorthand, not extra hypotheses.  MRP is the
middle-regime pinch tested numerically in d8.  A financier is a binding far row
in the finite families; it is not a universal role.  The budget line is the
family law \(H=2\delta\), while the flat floor is the finite-corner numerical
ratio \(\delta/H^2\approx3.49\).  A top band is a set of rows with small
canonical deficit \(g_i\), and a shallow web is a directed system of hidden
top-band rows witnessing one another.  Baake--Sumner refers here to the exact
\(\delta=0\) idempotent Markov normal form; the missing theorem is its signed
quantitative perturbative version.

Status badges are part of the mathematics.  A statement marked
\(\provedbadge\) has a recorded proof and survived the stated audit route.
A statement marked \(\modauditbadge\) is structurally proved or reduced but
still carries an explicit audit, constant, or banking qualification.
A statement marked \(\numbadge\) is verified computation, never a theorem.
Open claims are marked \(\openbadge\); false or withdrawn routes are marked
\(\refutedbadge\) or \(\downgradedbadge\).  No finite numerical pattern in this
report should be read as an asymptotic theorem unless it is explicitly proved
as one.  Badges in section heads or lead sentences are therefore not cosmetic;
they are part of the statement being made.

\paragraph{Roadmap.}
The first sections set up the signed affine-retraction model, the
\(\ell^1\) geometry of row polytopes, and the exposedness machinery.  They
also record two consumed main-project inputs as black-box theorems, not as
proofs reproduced in this report: the signed/stochastic equivalence and the
cluster assembly theorem, both with \(\provedbadge\) status in the ledger.
These imports are the reason the report may work with exact signed
idempotents while the target remains the original stochastic matrix problem.

The middle of the report gives the status table and the reduction chain.  The
current theorem-shaped progress is conditional.  \(\modauditbadge\)
HLC closes the exposed-hull problem.  \(\modauditbadge\) Existential DMF closes
HLC by the bound
\[
  H \leq \frac{\tau(2+4\delta)}{4m_*}+E(\delta),
\]
for a deep-witness mass \(m_*\) and depth error \(E(\delta)\).  If
\(E(\delta)/\tau\to e\), the resulting HLC constant is
\((1/(2m_*)+e)^{-2}\); the special \(4m_*^2\) asymptotic appears only when
\(E=o(\tau)\).  The report therefore treats HLC and DMF as the central
coordinates of the problem rather than as side terminology.

One finite feature receives its own section: the corner theorem.  The constants
\(\tau_*=2-\sqrt 3\), the wall \(2(2-\sqrt 3)\), and the floor
\((7+4\sqrt 3)/4\) explain a verified finite corner of the numerical
families.  \(\modauditbadge\) The closed forms are exact after the family laws
are accepted; \(\numbadge\) the optimality and finite-family gates are recorded
as computation.  They are not presented as an asymptotic proof of HLC.  This
distinction matters because later forensics reframe the old ``flat floor'' as
a finite-corner phenomenon, not a verified small-\(\delta\) law.

The audited belt collects the day-1 lemmas: lone far rows, hidden-vertex
extraction, the failed-exposedness dual, frame clipping, maximizer leakage,
the identity-frame linear bound, nilpotent-chain forcing, skinny
near-coincidence, and the fable-belt energy and rigidity facts.  Those results
are useful because they make the remaining obstruction small enough to name,
not because they independently prove the target theorem.

The wave-5--9 sections record the exposedness-dual identities, the sharp
witness exchange, row-witness and \(W\)-locality facts, and the
\(\sigtilde\)-height-collapse branch.  The post-design addendum strengthens
that branch: \(\provedbadge\) if \(\sigtilde\leq\tau\) and
\(\delta\leq1/4\), then
\[
  H\leq 2(1+2\delta)\max(\sigtilde,\nu_v)\leq 3\tau,
\]
so HLC follows directly there as \(\delta\geq H^2/9\).  In that branch
existential DMF is vacuous with \(m_*=1\) and \(C_D=3\).

The same addendum also prevents an overstrong formulation of the web problem.

\noindent\(\modauditbadge\) An exact rational \(5\times5\) certificate gives
an all-shallow optimal face with \(\sigtilde>0\) and the entire optimal witness
on a far row of deficit zero.  This exact rational certificate lives only at
height \(H=O(\delta)\).  Thus all-shallow faces are real; what remains open is
their exclusion at height comparable to \(\tau\).

The numerical section records verification gates rather than theorem claims.
\(\numbadge\) The reliable record through the final d13 small-\(\delta\)
verdict satisfies the linear law \(H\lesssim2\delta\); the formerly advertised
small-\(\delta\) flat floor was not verified below about \(\delta=0.06\).
D13 gives high-strength numerical confirmation of outcome (c): the apparent
floor is a finite-corner extrapolation, while the empirical small-\(\delta\)
law is linear.  This remains evidence and reframing, not a theorem.

The dead-route section is included so that later work does not accidentally
reuse refuted shortcuts.

\noindent\(\refutedbadge\) The literal psi-gap is false.  \(\downgradedbadge\)
Historical off-own-site wall language is downgraded unless restated with the
geometric \(\sigtilde\).  \(\provedbadge\) LP support-cleanup for shallow
witnesses is a dead end: pushing a witness through \(P\) introduces negative
leakage, and that leakage breaks dual optimality rather than producing depth.

The methodology section explains why the report is status-heavy.  Many claims
were rediscovered, audited, weakened, or refuted by independent workers.  The
goal of the write-up is therefore not to tell a smooth success story.  It is
to leave a compact map: what is proved, what is numerical, what is conditional,
what is false, and exactly where the remaining signed Baake--Sumner stability
problem sits.
