\section{Exposed Vertices, Hidden Height, And Separators}
\label{sec:geometry-exposedness}

This section fixes the geometric language used in the rest of the report.
The standing object is an exact signed affine retraction \(P\), so
\(P\one=\one\) and \(P^2=P\).  Its row \(i\) is \(p_i\), the row polytope
is \(K=\conv\{p_i:1\le i\le n\}\), the row negative mass is
\(\nu_i=\sum_k(P_{ik})_-\), and \(\delta=\max_i\nu_i\).  We set
\[
        \tau=\sqrt{\delta},\qquad \rho=4\tau,\qquad \kappa=\tau/4 .
\]
All distances below are \(\ell^1\)-distances, written \(\distone\).

A row vertex \(p_v\) is \emph{\((\rho,\kappa)\)-exposed} if some affine
test function \(h\) on the row set has \(0\le h(p_i)\le1\) for all \(i\),
\(h(p_v)=0\), and \(h(p_i)\ge\kappa\) whenever
\(\|p_i-p_v\|_1\ge\rho\).  Let \(\W\) be the set of such row vertices and
put \(C_W=\conv\{p_w:w\in\W\}\).  Rows outside this exposed hull are
\emph{hidden}; a hidden row vertex attaining the maximal distance to
\(C_W\) is a \emph{hidden top vertex}.  The hidden height is
\(H=\max_i\distone(p_i,C_W)\).  Since distance to a convex set is convex,
the maximum may be sought on row vertices.

For a chosen hidden top vertex \(v\), a \emph{canonical separator} is an
affine functional \(\phi\) with \(\|\nabla\phi\|_\infty\le1\),
\(\phi(x)\le0\) for \(x\in C_W\), \(\sup_{x\in C_W}\phi(x)=0\), and
\(\phi(p_v)=H\).  The associated \emph{deficit} is
\(g_i=H-\phi(p_i)\), with \(g=(g_i)_i\).  In the canonical setup
\(g=Pg\); also \(g_v=0\), while topness gives \(g_i\ge0\) for every
row.  The deficit oscillation is
\[
        \Omega_g=\max_i g_i-\min_i g_i .
\]
\begin{lemma}
\provedbadge\label{lem:omega-g-bound}
For the canonical deficit vector, \(\Omega_g\le 2+4\delta\).
\end{lemma}

\begin{proof}
For rows \(i,j\), \(g_i-g_j=\phi(p_j)-\phi(p_i)\), and the dual
normalization gives \(|\phi(p_i)-\phi(p_j)|\le\|p_i-p_j\|_1\).  Since
\(\|p_i\|_1=1+2\nu_i\le1+2\delta\), we have
\(\|p_i-p_j\|_1\le\|p_i\|_1+\|p_j\|_1\le2+4\delta\).
\end{proof}
The source notes often wrote a bare \(R\) for this oscillation.  This
report uses \(\Omega_g\) to avoid collision with the frame matrix
\(\framemat\).

The positive carrier set of \(v\) is \(\Av=\{k:P_{vk}>0\}\).  For a
selected \(T\subseteq\Av\), its carrier mass and normalized weights are
\(\sigma_T=\sum_{k\in T}P_{vk}\) and
\(\lambda_k=P_{vk}/\sigma_T\) when \(\sigma_T>0\).  The own-site positive
mass is \((P_{vv})_+\), while the formal off-own-site positive mass is
\[
        \sigoff=\sum_{k\ne v}(P_{vk})_+ .
\]
This formal quantity is not the robust branch variable.  The robust
quantity is geometric: for \(\varepsilon\ge0\),
\[
        \widetilde\sigma_v(\varepsilon)
        =\sum_{\substack{k:\,P_{vk}>0\\ \distone(p_k,C_W)>\varepsilon}} P_{vk}.
\]
We write \(\sigtilde=\widetilde\sigma_v(0)\) when no halo is being used.
In the report convention the self-row is included in this sum if
\(P_{vv}>0\) and \(p_v\notin C_W\).  Rows in the
\(\varepsilon\)-halo of \(C_W\) are treated as already deep: if
\(\distone(p_k,C_W)\le\varepsilon\), then
\(\phi(p_k)\le\varepsilon\) and hence \(g_k\ge H-\varepsilon\).

\medskip
\noindent\fbox{%
\begin{minipage}{0.94\linewidth}
\textbf{Notation clash audit.}
The report never uses an unqualified sigma symbol for \(v\).  The symbol
\(\sigoff\) means formal off-own-site positive mass, while \(\sigtilde\)
means positive carrier mass geometrically outside \(C_W\), with the
\(\varepsilon\)-halo convention above.  Index-not-in-\(W\) mass is only a
numerical proxy used in some d12 records.  The report also writes
\(\Omega_g\), not the source-note \(R\), for the oscillation of \(g\).
\end{minipage}}

\begin{lemma}
\provedbadge\label{lem:W-rows-deep}
For the canonical separator of a hidden top vertex \(v\), every
\(W\)-row is deep: if \(w\in\W\), then \(g_w\ge H\).
\end{lemma}

\begin{proof}
Since \(p_w\in C_W\), \(\phi(p_w)\le0\), so \(g_w=H-\phi(p_w)\ge H\).
\end{proof}

The exposedness LP for \(v\) maximizes \(t^*(v)\) over affine tests with
\(0\le h\le1\), \(h(p_v)=0\), and \(h(p_j)\ge t\) on
\(F_v=\{j:\|p_j-p_v\|_1\ge\rho\}\).  With \(d_i=p_i-p_v\) and
\(h(p_i)=u\cdot d_i\), its finite primal is
\[
        \max_{u,t} t\quad\text{s.t.}\quad
        t-u\cdot d_j\le0\ (j\in F_v),\quad
        -u\cdot d_k\le0,\quad u\cdot d_k\le1\ (1\le k\le n),
\]
with \(u\) free.  Its dual minimizes \(B=\sum_k\beta_k\), subject to
\(\mu_j,\alpha_k,\beta_k\ge0\), \(\sum_{j\in F_v}\mu_j=1\), and
\[
        \sum_{j\in F_v}\mu_jp_j+\sum_k\alpha_kp_k
        =\sum_k\beta_kp_k+(1+A-B)p_v,\qquad A=\sum_k\alpha_k .
\]
Thus \(v\) fails exposedness exactly when \(t^*(v)<\kappa\).  Here
\(\mu\) prices far-row margins, \(\alpha\) lower boxes \(h\ge0\), and
\(\beta\) upper boxes \(h\le1\); \(\gamma=1+A-B\) is just the produced
\(p_v\)-coefficient.  In an optimal dual witness, \(B=t^*(v)\).

\begin{warning}
\provedbadge\label{warn:feasible-optimal-gap}
The exchange estimate uses the witness actually chosen.  For a merely
feasible dual witness it bounds its own \(B\,\Omega_g\), not
\(t^*(v)\Omega_g\).  Replacing \(B\) by \(t^*(v)\) is justified only on
the optimal dual face.
\end{warning}

\begin{warning}
\downgradedbadge\label{warn:old-sigma}
The historical sigma-wall language is ambiguous.  In the corner family,
the formal off-own-site mass \(\sigoff\) is about one, while the intended
branch mass is geometric non-\(C_W\) carrier mass, now recorded as
\(\sigtilde\).  Some numerical logs measured the index-not-in-\(W\)
proxy instead.  Old branch statements using an unqualified sigma symbol
must be read as downgraded until restated with geometric \(\sigtilde\).
\end{warning}

\begin{proposition}
\provedbadge\label{prop:sigtilde-height-cap}
Let \(v\) be a hidden top vertex and put \(s=\sigtilde\).  Then the
barycenter split gives
\[
        H\le 2(1+2\delta)\max(s,\nu_v).
\]
In particular, if \(s\le\tau\) and \(\delta\le1/4\), then
\[
        H\le 3\tau,\qquad\hbox{so}\qquad \delta\ge H^2/9 .
\]
With \(m_*=1\) and \(C_D=3\), existential DMF is then vacuous on this
branch because \(H-3\delta/\tau\le0\).
\end{proposition}

\begin{proof}
Split the positive part of the row identity for \(p_v\) into carriers in
\(C_W\), of mass \(1+\nu_v-s\), and carriers outside \(C_W\), of mass
\(s\).  Normalize the inside part to a point \(c\in C_W\).  Every row has
\(\ell^1\)-norm at most \(1+2\delta\).  The coefficient mismatch between
\(p_v\) and \(c\) has size \(s+\nu_v+|s-\nu_v|\), hence
\[
        H\le\|p_v-c\|_1
        \le (s+\nu_v+|s-\nu_v|)(1+2\delta)
        \le 2(1+2\delta)\max(s,\nu_v).
\]
The final inequalities use \(\nu_v\le\delta=\tau^2\le\tau\) and
\(2(1+2\delta)\le3\) when \(\delta\le1/4\).
\end{proof}

\begin{warning}
\modauditbadge\label{warn:all-shallow-height}
All-shallow optimal faces do exist, but only in the height scale seen so
far at \(H=O(\delta)\).  In the report's one-based indexing, the exact
rational \(5\times5\) construction has \(W=\{1,2,3\}\), hidden vertices
\(4,5\), \(\sigtilde=1/2000>0\), \(H=1/1000\), and for \(v=4\) the
entire optimal dual witness lies on the far shallow row \(5\) with
\(g_5=0\).  This proves the low-height existence certificate modulo audit,
while the height-\(\tau\) web exclusion remains open; it does not refute DMF
with a slack of order \(\delta/\tau\).
\end{warning}

\begin{warning}
\provedbadge\label{warn:pushed-witness}
The pushed-witness calculation is a death certificate for LP
support-cleanup as a proof strategy for the remaining branch.  If an
optimal shallow witness is pushed through \(P\), negative leakage changes
the normalized dual objective to
\[
        B_{\rm pushed}=\frac{B+N}{M_F},
\]
where \(N\) is the pushed negative leakage and \(M_F\le1+N\) is the
positive mass returning to the far set.  When \(B=t^*(v)>0\), optimality
would require \(M_F\ge1+N/B\), impossible for \(N>0\) and \(B<\kappa<1\).
When \(t^*(v)=0\), the exchange handles the chain case without division by
\(B\).  Thus support cleanup is dead-route guidance, not a proof route.
\end{warning}

\begin{numericalresult}
\numbadge\label{num:d12-and-floor}
The d12 witness probe measured an index-based proxy for \(\sigtilde\):
positive mass on indices not in \(W\).  On its verified financed wiggle
instances this proxy was zero, so the row-witness was supported on
\(W\)-rows and was deep by \cref{lem:W-rows-deep}; this is evidence for
that corner-scale family only.  The d13 final verdict was outcome (c):
no verified hidden-top-vertex floor instance for \(\delta\le10^{-2}\),
with achieved heights tracking the linear law \(H\approx2\delta\).
\end{numericalresult}

\begin{openproblem}
\openbadge\label{open:height-conditional-web}
The remaining hidden-localization problem is the height-qualified web
case: exclude hidden top vertices with \(\sigtilde>\tau\) and \(H>B\tau\)
for a universal \(B\).  Equivalently, HLC is reduced to signed
quantitative Baake--Sumner stability: a shallow hidden web carrying
almost all positive mass must either collapse to height \(O(\delta)\) or
produce a deep optimal witness.
\end{openproblem}
