\section{Main Results and Status Ledger}

This section is the report's status contract.  A row means a row \(p_i\) of
the exact signed affine retraction \(P\), where \(P\one=\one\) and \(P^2=P\).
The row negative mass is \(\nu_i\), its maximum is \(\delta\), and
\(\tau=\sqrt{\delta}\).  The set \(\W\) consists of the
\((\rho,\kappa)\)-well-exposed row vertices, with \(\rho=4\tau\) and
\(\kappa=\tau/4\), and the hidden height is
\[
  H=\max_i \distone(p_i,\conv(\W)).
\]
The hidden localization claim, abbreviated HLC, asks for a universal
constant \(a>0\) such that \(\delta\ge aH^2\).

The badges below are part of the statement.  \(\provedbadge\) means a proof
survived the stated audit; \(\modauditbadge\) means the proof exists with an
explicit caveat or banking condition; \(\numbadge\) is verified computation,
not a theorem; \(\openbadge\) is unresolved; \(\refutedbadge\) is false; and
\(\downgradedbadge\) means an earlier stronger reading was withdrawn.

\subsection{Main chain}

\begin{longtable}{p{0.22\linewidth}p{0.16\linewidth}p{0.52\linewidth}}
\toprule
Entry & Status & What this report may state \\
\midrule
\texttt{op-classical}
& \openbadge
& Dimension-free stability of almost-idempotent row-stochastic matrices is
the outer target.  It is not closed in this exploration. \\
\texttt{lem-classical-equiv}
& \provedbadge
& The stochastic-idempotent formulation and the signed-idempotent
formulation are equivalent; the report consumes this main-project result. \\
\texttt{thm-cluster}
& \provedbadge
& The classical target reduces to the clustering plus exposed-hull route;
only this contract-level fact is imported here. \\
\texttt{op-exposed-hull}
& \openbadge
& The global exposed-hull problem remains open as a standalone target. \\
\texttt{op-exposed-hull} from HLC
& \modauditbadge
& If HLC holds with \(\delta\ge aH^2\), then exposed-hull stability follows;
``two-family verified assembly'' means independent derivations from two model
families plus hostile audit, not a separate theorem hidden from the reader. \\
\texttt{HLC}
& \openbadge
& HLC is the terminal mathematical target in this report.  It is supported by
the record but remains unproved. \\
\texttt{existential-DMF suffices}
& \modauditbadge
& One optimal failed-exposedness witness with deep mass is enough:
if a witness has \(\mu\)-mass at least \(m_*\) at deficit
\(g\ge H-E(\delta)\), then
\[
  H\le E(\delta)+\frac{\tau(2+4\delta)}{4m_*}.
\]
If \(E(\delta)/\tau\to e\), the resulting HLC constant is
\((e+1/(2m_*))^{-2}\). \\
\texttt{DMF}
& \openbadge
& Deep-witness mass forcing itself is open in the high-web branch.  The
post-design refinement uses existential DMF: one optimal witness, not every
feasible witness, must carry the deep mass. \\
\texttt{quantitative Baake-Sumner web stability}
& \openbadge
& The remaining structural input is a signed, quantitative stability theorem
excluding hidden top vertices with \(\sigtilde>\tau\), \(H>B\tau\), and only
shallow top-band witnesses.  The exact \(\delta=0\) Baake--Sumner anchor is
banked, but the perturbative theorem is not. \\
\bottomrule
\end{longtable}

\subsection{Post-design sharpenings}

The final branch variable is the geometric non-\(\W\) positive mass.  For a
row \(x\), write \(C_W=\conv(\W)\) and measure positive mass on rows at
positive \(\ell^1\)-distance from \(C_W\); with an \(\varepsilon\)-halo this
is \(\widetilde{\sigma}_x(\varepsilon)\).  Halo rows with
\(\distone(p_j,C_W)\le\varepsilon\) are automatically
\((H-\varepsilon)\)-deep for the canonical deficit \(g_i=H-\phi(p_i)\).
The older index-based proxy used by d12 is therefore evidence for those
instances, but it is not the canonical definition of \(\sigtilde\).

\begin{longtable}{p{0.22\linewidth}p{0.16\linewidth}p{0.52\linewidth}}
\toprule
Entry & Status & Current form \\
\midrule
\(\sigtilde\le\tau\) branch
& \provedbadge
& If \(v\) is a hidden top vertex, then
\[
  H\le 2(1+2\delta)\max(\sigtilde,\nu_v).
\]
Thus \(\sigtilde\le\tau\) and \(\delta\le 1/4\) imply
\(H\le3\tau\), hence \(\delta\ge H^2/9\) directly.  In this branch
existential DMF is vacuous with \(m_*=1\) and \(C_D=3\). \\
All-shallow optimal face
& \modauditbadge
& An exact rational \(5\times5\) construction has hidden rows,
\(\sigtilde>0\), and an optimal failed-exposedness witness supported
entirely on a far row with \(g=0\).  The certificate is exact-rational with
mod-audit status, and it lives on \(H=O(\delta)\).  It refutes any absolute ban
on all-shallow witnesses, but not the height-comparable-to-\(\tau\) web
exclusion needed for HLC. \\
Pushed-witness cleanup
& \provedbadge
& LP support cleanup has a proved death certificate as a proof route.  For
an optimal witness with \(B=t^*(v)>0\), pushing shallow witness rows through
\(P\) changes the dual objective to \((B+N)/M_F\); negative leakage \(N>0\)
prevents the pushed witness from staying optimal.  The \(t^*(v)=0\) case is
handled separately by the exchange inequality, without division by \(B\). \\
Feasible versus optimal witnesses
& \downgradedbadge
& A deep row-witness is not enough by itself.  The exchange inequality bounds
a feasible witness by its own objective value, so depth must occur on an
optimal face or be transferred to one with proof. \\
Final web form
& \openbadge
& Since the \(\sigtilde\le\tau\) branch is proved, HLC is reduced to
excluding hidden top vertices with \(\sigtilde>\tau\) and height larger than
a fixed universal multiple of \(\tau\).  This is the signed quantitative
Baake--Sumner stability problem. \\
\bottomrule
\end{longtable}

\subsection{Corner, numerical record, and retractions}

\begin{longtable}{p{0.22\linewidth}p{0.16\linewidth}p{0.52\linewidth}}
\toprule
Entry & Status & Current form \\
\midrule
Corner closed forms
& \modauditbadge\ \numbadge
& The measured corner family has
\[
  \tau_*=2-\sqrt3,\qquad
  \delta_*=(2-\sqrt3)^2,\qquad
  \delta/H^2=(7+4\sqrt3)/4
\]
at the finite corner.  The algebraic constants are exact for the family;
the relevant optimality and family equality are numerical or mod-audit. \\
Finite-corner calibration
& \downgradedbadge
& The finite corner does not prove an asymptotic HLC constant.  Earlier
claims that \(m_*=1\) DMF reproduced the whole measured envelope were
retracted after the \(\Omega_g\)-handling correction. \\
Historical \(\sigma\)-wall
& \downgradedbadge
& Older notes overloaded the external-mass variable.  Future mathematical
statements must distinguish the formal off-own-site mass \(\sigoff\) from
the geometric non-\(\W\) mass \(\sigtilde\). \\
d12 DMF support
& \downgradedbadge\ \numbadge
& D12 found fully deep optimal witnesses in its verified instances, but its
scope is corner or budget-line only.  It does not settle the small-\(\delta\)
web case. \\
Flat-floor interpretation
& \downgradedbadge\ \numbadge
& The apparent \(\delta/H^2\approx3.49\) floor was not verified below
\(\delta\approx0.06\).  The saved small-\(\delta\) record collapses to the
linear law \(H\approx2\delta\), not to \(H\asymp\sqrt{\delta}\). \\
\bottomrule
\end{longtable}

\begin{numericalresult}
\numbadge
Across the verified record, including the exact-instance campaigns, the d8
middle-regime decider, d11 scale sweeps, d12 witness-depth probes, and the
final d13 small-\(\delta\) search, no counterexample to HLC is known.  The
empirical reframing is stronger: every verified instance in the record
satisfies \(H\lesssim2\delta\), the day-1 linear hull-distance law.  D13
records outcome (c): the flat floor is a finite-corner extrapolation, and the
linear law is the empirical small-\(\delta\) behavior.  This is evidence only.
\end{numericalresult}

\begin{refutedstatement}
\refutedbadge
Several earlier routes are not available as theorems: the literal uniform
psi-gap is false; the general-row leakage statement is false outside a
global height maximizer; literal ``no far top-band row'' localization is
false; raw factorization-gauge arguments are not invariant; and finite
corner constants cannot be used as an asymptotic proof.
\end{refutedstatement}

\begin{openproblem}
\openbadge
Final residual.  Prove, or refute by construction, the height-conditional
web exclusion: a hidden top vertex with \(\sigtilde>\tau\) cannot sit at
height comparable to \(\tau\) while all optimal failed-exposedness witnesses
remain shallow.  Equivalently for this report's chain, prove the signed
quantitative Baake--Sumner stability needed to rule out such shallow hidden
webs.  A low-height all-shallow face is known, so the statement must be
height-conditional.
\end{openproblem}

Later sections give the proofs, audits, numerical gates, and dead-route
details.  This section is only the inventory: it records what is proved, what
is conditional, what is numerical, and what remains open.
