\section{The audited day-1 belt}

The day-1 belt is a toolkit of local facts about an exact signed affine
retraction \(P\), meaning \(P\one=\one\) and \(P^2=P\), whose rows are
points \(p_i\) in the row polytope \(K=\conv\{p_i\}\).  The row negative
mass is \(\nu_i=\sum_k(P_{ik})_-\), the global small parameter is
\(\delta=\max_i\nu_i\), and \(\tau=\sqrt\delta\).  The exposed geometry
uses \(\rho=4\tau\) and \(\kappa=\tau/4\).  A row vertex is
well-exposed if an affine test function separates it from all
\(\rho\)-far rows by margin at least \(\kappa\); \(\W\) is the set of
well-exposed row vertices, \(C_W=\conv(\W)\), and
\[
        H=\max_i \distone(p_i,C_W)
\]
is the hidden height.  A hidden top vertex is a row vertex \(v\) attaining
this maximum.  For such \(v\), the canonical separator \(\phi\) is the
normalized \(\ell^\infty\)-dual affine functional with \(\phi=0\) on
\(C_W\) and \(\phi(p_v)=H\), and the deficit vector is
\(g_i=H-\phi(p_i)\), with oscillation \(\Omega_g=\max_i g_i-\min_i g_i\).
The hidden localization claim (HLC) asks for a dimension-free constant
\(a>0\) with \(\delta\ge aH^2\).

The belt below is not the proof of hidden localization.  It records the
audited local moves that survived the first day, together with the exact
caveats that stop them from closing the problem.

\subsection{First local facts}

\begingroup
\small
\begin{longtable}{p{0.16\linewidth}p{0.20\linewidth}p{0.51\linewidth}}
\toprule
Fact & Status & What is banked for the report \\
\midrule
L1 lone-far-row & \provedbadge &
If a row is at \(\ell^1\)-distance at least \(\rho\) from the hull of all
other rows, it is exposed with margin at least
\(\rho/(2+4\delta)\).  The constant uses the signed-row diameter bound
\(D_K\le 2+4\delta\). \\
L2 far/high row to vertex & \provedbadge &
A height or farness witness may be chosen at a row vertex.  This is a
convexity reduction, not an iteration scheme. \\
L2' \(\rho\)-shadow & \modauditbadge &
A hidden vertex has a \(\rho\)-shadow, meaning a point of the hull of
the other rows within \(\rho\).  The attempted recursion to a new hidden
vertex is not banked without an extra no-reuse input. \\
C10 failed-exposedness dual & \provedbadge &
If the exposedness LP for \(v\) has optimum \(t^*(v)<\kappa\), there is
a dual witness \((\mu,\alpha,\beta,\gamma)\).  The identity is proved;
controlling the total alpha mass \(A=\sum_i\alpha_i\) is still the old
crux. \\
L4 frame-clipping & \provedbadge &
Signed coefficient mass clips distance to a convex frame: after
separating positive and negative coefficients, a row lies within
\((2+4\delta)\nu_i\) of the corresponding positive hull. \\
L5' leakage at global maximizer & \modauditbadge &
At a global height maximizer only, positive coefficient leakage from the
top level to rows below \(H/2\) is \(O(\delta/H)\).  The corresponding
statement for an arbitrary row is false. \\
L6 identity-frame linear bound & \modauditbadge &
In the identity realization \(\framemat=[I\mid 0]\), coordinate
negative mass equals realized row negative mass, so \(\delta\ge H/2\).
The transfer of this linear estimate to a general frame is open. \\
N1 nilpotent-chain forcing & \provedbadge &
An acyclic high chain cannot reproduce height using only lower rows:
nilpotence forces substantial positive mass to off-chain high rows
unless the negative mass is already large. \\
F1 skinny near-coincidence & \provedbadge &
For two mutually shadowing high rows under the stated hypotheses, the
scalar exactness relations force the skinny degeneracy
\(1-\mu_1\mu_2=O(\rho/H)\).  This explains why the projection-norm route
alone does not close the residual. \\
X1 one-mode wall & \provedbadge &
In an exact one-mode shell \(p_i=q+t_i r\), biorthogonality forces
diameter at least \(2\).  Thus a nonconstant high mode cannot stay
inside a sub-\(\rho\) skinny cluster. \\
X2 stochastic-complement rank preservation & \provedbadge &
The exact stochastic complement \(A+B(I-D)^{-1}C\), when defined,
remains row-stochastic and idempotent and preserves rank.  This is useful
as an obstruction to naive rank induction, not as a closure. \\
\bottomrule
\end{longtable}
\endgroup

These facts explain why the first easy geometries fail.  Lone isolated
vertices expose; exact one-mode shells hit a wall; and acyclic chains
must feed height into other high rows.  What remains is not absence of
local structure, but the possibility that the structure circulates inside
a shallow hidden web.

\subsection{The fable belt after audit}

The fable pass introduced a second layer of local estimates.  In this
table, a shadow is a near representation by other rows, a blocker is a
\(\rho\)-far row that binds an exposedness separator, and an \(S\)-full
row is one with almost all its mass on a selected site set \(S\).  The
word self-indexed means that row labels also serve as coefficient
coordinates.  For a selected row \(v\),
\(\sigoff=\sum_{k\ne v}(P_{vk})_+\) is the formal positive mass away
from its own row coordinate.  The
wave-4 audit controls the constants used here; when the original fable
has a stronger number, the audited number wins.

\begingroup
\small
\begin{longtable}{p{0.14\linewidth}p{0.19\linewidth}p{0.54\linewidth}}
\toprule
Fact & Status & Audited content \\
\midrule
F-SS sharp shadow & \provedbadge &
Rows with nontrivial self-defect, meaning \(P_{ii}<1\), have small
shadows in the hull of the other rows, at scale
\(O(\delta/(1-P_{ii}))\). \\
F-ND near-delta exposure & \provedbadge &
Rows whose formal off-own-site mass \(\sigoff\) is small enough are
forced into exposed clusters.  The safe audited constant is conservative,
about \(0.85\), rather than the sharper fable value. \\
F-E kernel energy & \provedbadge &
The classical kernel-energy object is
\[
        \Gamma=P(g^2)-g^2,
\]
where \(g^2\) is coordinatewise.  It satisfies \(P\Gamma=0\), and its
starvation/localization bounds carry explicit \(\Omega_g\)-dependence. \\
F-GB deficit budget & \provedbadge &
If a row places positive coefficient mass at deficit level at least
\(\ell\), then the product of that mass with \(\ell\) is bounded by
\(g_j+\delta\Omega_g\).  The original constant-only version is not used
without an independent oscillation bound. \\
F-WR wiggle rigidity & \modauditbadge &
Common-pattern self-indexed webs, meaning mutually shadowing hidden rows
with matching coefficient patterns, obey a rigidity estimate; closed
webs coincide up to the stated error.  The side conditions are part of
the result: self-indexing, small \(\delta\), and, for the separation
corollary, a web-radius bound. \\
F-BC blocker cap & \provedbadge &
An \(S\)-full blocker has at most \(\kappa+\delta\) external coefficient
mass.  This is stronger than the fable constant after audit. \\
F-2R private two-shell collapse & \modauditbadge &
Exact private two-shell configurations collapse to coincident
equal-input classes in the private-site case, where the two shells use
disjoint private sites. \\
\bottomrule
\end{longtable}
\endgroup

The original F-\(\psi\) route is not part of the proved belt.
\(\downgradedbadge\) The uniform \(\psi\)-gap/max-selection statement was
not confirmed by the audit.  \(\refutedbadge\) The literal gap was later
refuted: a \(\rho\)-far non-\(S\)-full row can trade \(S\)-deficit
against the separator term.  \(\modauditbadge\) There is a conditioned
canonical-\(\W\) replacement elsewhere, but it reroutes into the same
residual rather than closing it.

\subsection{What the belt leaves open}

The belt narrows the obstruction but does not remove it.  The failed
exposedness dual gives witnesses, the energy object localizes only where
\(\Omega_g\) is controlled, and the leakage facts control high-to-low
escape but not a high-to-high circulation of hidden rows.  In the day-1
language \(\openbadge\) this was the middle-regime pinch; after the
later synthesis it is cleaner to call it the shallow hidden-witness web.

For later sections, \(\sigtilde\) is the geometric non-\(W\) positive
carrier mass: positive coefficient mass on rows outside \(C_W\), with an
\(\epsilon\)-halo treated as depth slack.  The post-design synthesis
records \(\provedbadge\) the branch \(\sigtilde\le\tau\): the height cap
\[
        H\le 2(1+2\delta)\max(\sigtilde,\nu_v)
\]
gives \(H\le 3\tau\) when \(\delta\le 1/4\), hence \(\delta\ge H^2/9\)
directly on that branch.  It also records \(\modauditbadge\) an
audit-pending exact rational \(5\times 5\) all-shallow optimal face,
meaning an optimal failed-exposedness witness face whose \(\mu\)-mass
stays away from deep rows with deficit near \(H\).  This construction has
\(\sigtilde>0\), but only at height \(H=O(\delta)\); it warns that
shallow webs cannot be excluded absolutely.

Thus the final open should be read height-conditionally:
\(\openbadge\) HLC is equivalent to excluding hidden top vertices with
\(\sigtilde>\tau\) at height \(H>B\tau\), i.e. to a signed quantitative
Baake--Sumner stability statement: a stability version of the exact
equal-input idempotent Markov normal form for signed shallow webs.
\(\numbadge\) The empirical record has not verified a flat floor below
\(\delta\approx 0.06\); every verified instance in the record satisfies
the stronger linear pattern \(H\lesssim 2\delta\).  \(\openbadge\) The
final small-\(\delta\) probe d13 remains [pending], so this section uses
the belt only as audited structure, not as an asymptotic theorem.
