\section{DMF, Shallow Webs, And The Remaining Open}
\label{sec:residual-dmf}

\subsection{The Residual}

Work in the exact signed affine retraction model: \(P\one=\one\),
\(P^2=P\), with rows \(p_i\), row negative masses \(\nu_i\), maximal
negative mass \(\delta=\max_i\nu_i\), and \(\tau=\sqrt{\delta}\).
Let \(\W\) be the set of well-exposed row vertices and put
\[
  C_W=\conv(\W),\qquad H=\max_i\distone(p_i,C_W).
\]
For \(H>0\) choose a hidden top vertex \(v\), meaning a row vertex attaining
this maximum and not lying in \(C_W\).  Its canonical separator is an affine
functional \(\phi\), normalized in the \(\ell^\infty\) dual, with
\(\phi\le0\) on \(C_W\) and \(\phi(p_v)=H\).  The deficit is
\[
  g_i=H-\phi(p_i),\qquad \Omega_g=\max_i g_i-\min_i g_i .
\]
For a top vertex the audited setup gives \(g_i\ge0\) for all rows and
\(g=Pg\).  Rows of \(\W\) are automatically deep in the sense below, because
\(\phi(p_w)\le0\) implies \(g_w\ge H\).

The exposedness LP for \(v\) has optimal margin \(t^*(v)\).  When \(v\) is
not exposed, an optimal failed-exposedness witness is a dual certificate
\((\mu,\alpha,\beta,\gamma)\), where \(\mu\) is a probability measure on the
\(\rho\)-far rows \(F_v\), \(\alpha,\beta\ge0\), and the dual identity gives
the sharp exchange
\[
  \sum_j\mu_j g_j+\sum_i\alpha_i g_i
  =\sum_k\beta_k g_k
  \le t^*(v)\,\Omega_g<\kappa\Omega_g .
\]
This exchange is the pricing mechanism: it can turn witness depth into a
height bound, but it does not create depth by itself.

\subsection{Deep-Witness Mass Forcing}

For constants \(m_*\in(0,1]\) and an error width \(E(\delta)\), a row
\(j\) is \(E\)-deep for \(v\) if \(g_j\ge H-E(\delta)\).  The universal
deep-witness mass-forcing statement says that every hidden top vertex \(v\)
and every optimal failed-exposedness witness for \(v\) satisfy
\[
  \mu\{j:g_j\ge H-E(\delta)\}\ge m_* .
\]
The existential form requires only one optimal witness with this much deep
mass.  This distinction is now load-bearing: the HLC chain needs only the
existential form, while feasible row witnesses do not help unless they are
proved to lie on, or transfer to, the optimal dual face.

\begin{proposition}[Existential DMF suffices for HLC]
\modauditbadge
Assume existential DMF holds for all sufficiently small \(\delta\), with
parameters \(m_*>0\) and \(E(\delta)\).  Then every hidden top vertex obeys
\[
  H\le E(\delta)+\frac{\tau(2+4\delta)}{4m_*}.
\]
Consequently, if \(E(\delta)/\tau\to e\), then HLC follows with asymptotic
constant
\[
  a=\left(\frac{1}{2m_*}+e\right)^{-2};
\]
in particular \(E=o(\tau)\) gives \(a\to4m_*^2\).
\end{proposition}

\begin{proof}
Choose an optimal witness carrying mass \(m_*\) on \(E\)-deep rows.  Since
\(\alpha_i g_i\ge0\), the sharp exchange gives
\[
  m_*(H-E(\delta))
  \le \sum_j\mu_jg_j
  \le t^*(v)\Omega_g<\kappa\Omega_g .
\]
Here \(\kappa=\tau/4\) and the top-separator normalization gives
\(\Omega_g\le2+4\delta\).  Rearranging gives the displayed height bound.  If
\(t^*(v)=0\), the same exchange forces \(\sum_j\mu_jg_j=0\), hence DMF gives
\(H\le E(\delta)\), so no separate positive-margin case is needed.
\end{proof}

The full DMF statement remains open.  The proved part is the small
geometric-\(\widetilde\sigma_v\) branch.  Here
\(\widetilde\sigma_v(\varepsilon)\) denotes the positive coefficient mass
of row \(v\) on rows whose \(\ell^1\)-distance from \(C_W\) is greater than
\(\varepsilon\); rows in the \(\varepsilon\)-halo are automatically
\((H-\varepsilon)\)-deep.  At \(\varepsilon=0\) this is the report's
geometric branch variable, not the older index-based \(\sigoff\).

\begin{lemma}[Small-\(\widetilde\sigma_v\) height cap]
\provedbadge
For a hidden top vertex \(v\),
\[
  H\le 2(1+2\delta)\max(\widetilde\sigma_v,\nu_v).
\]
Thus, if \(\widetilde\sigma_v\le\tau\) and \(\delta\le1/4\), then
\[
  H\le3\tau,\qquad \delta\ge H^2/9.
\]
In the same branch existential DMF holds vacuously with \(m_*=1\) and
\(E(\delta)=3\delta/\tau\).
\end{lemma}

\begin{proof}
Split the positive part of \(p_v\) into mass on \(C_W\) and mass
\(\widetilde\sigma_v\) outside \(C_W\).  Normalize the \(C_W\)-part to a
barycenter \(c\in C_W\).  Since every row has \(\ell^1\)-norm at most
\(1+2\delta\), the distance from \(p_v\) to \(c\) is bounded by
\(2(1+2\delta)\max(\widetilde\sigma_v,\nu_v)\).  This bounds
\(\distone(p_v,C_W)=H\).  Under \(\widetilde\sigma_v\le\tau\) and
\(\delta\le1/4\), also \(\nu_v\le\delta\le\tau\), so \(H\le3\tau\).  Then
the depth threshold \(H-3\delta/\tau=H-3\tau\) is nonpositive, while
\(g_j\ge0\) for all rows.
\end{proof}

\subsection{Shallow Webs}

An all-shallow optimal witness is an optimal failed-exposedness witness whose
\(\mu\)-mass avoids the \(E\)-deep rows.  A shallow hidden web is a directed
system of hidden top-band rows in which each row is witnessed by other
shallow hidden rows rather than by rows of \(\W\).  The word ``web'' is meant
literally here: the obstruction is not one bad row, but a self-sustaining
top-band component.

\begin{proposition}[Partial web exclusions]
\modauditbadge
Wave-9 excludes three simple web mechanisms: direct two-site mutual carrying
above \(1/2+O(\delta)\), closed disjoint order-one two-ball cycles under the
return-mass inequality, and non-skinny payment patterns, where the latter
already force \(\delta\ge cH^2\).  The skinny spread-mass regime remains
open.
\end{proposition}

\begin{proposition}[Low-height all-shallow faces exist]
\modauditbadge
There is an exact rational \(5\times5\) signed idempotent certificate with
\(\widetilde\sigma_v>0\) and an optimal witness supported entirely on a far
row with \(g=0\).  This does not refute DMF with \(E=C_D\delta/\tau\), because
the construction has \(H=O(\delta)\), hence \(H/\tau\to0\).  Therefore the
web exclusion must be height-conditional, not absolute.
\end{proposition}

The contrapositive of the small-\(\widetilde\sigma_v\) height cap explains
why the web case is the only remaining high-height scenario.  If
\(H\gg\delta\), the positive mass of \(v\) on \(C_W\) is at most
\(\delta\Omega_g/H\), so \(\widetilde\sigma_v\) is forced close to \(1\).
Thus a small-\(\delta\) counterexample to the hoped-for linear law, or to HLC
through the DMF route, must be an almost-closed shallow hidden web with
\(\widetilde\sigma_v>\tau\) and \(H\) comparable to \(\tau\).

\begin{warning}[Pushing witnesses does not close the web case]
\provedbadge
LP support cleanup cannot prove the remaining branch.  If a shallow optimal
witness is pushed through \(P\), the pushed dual objective becomes
\[
  B_{\mathrm{pushed}}=\frac{B+N}{M_F},
\]
where \(N\) is the negative leakage and \(M_F\le1+N\) is the pushed far mass.
Optimality would require \(M_F\ge1+N/B\), impossible for \(N>0\) because
\(B=t^*(v)<\kappa<1\).  The missing input is therefore not another
exposedness-dual algebra trick.
\end{warning}

\subsection{Numerical Status And Literature Position}

\begin{numericalresult}[D12 depth profiles]
\numbadge
In twelve verified financed-wiggle instances, all optimal witnesses were
deep with observed \(m_*=1\), and the measured index-based non-\(W\) carrier
mass was zero.  Post-w9 and swarm audits downgrade the scope: those instances
lie on the \(H=O(\delta)\) budget line, so they do not measure the
high-height web branch.
\end{numericalresult}

The empirical reframing is sharper than the original flat-floor story.  The
verified record has not established a small-\(\delta\) floor with
\(H\asymp\tau\); all verified instances in the record satisfy roughly
\(H\le2\delta\).  The final small-\(\delta\) probe is still pending, so the
report should treat the linear law \(H=O(\delta)\) as a conjectural target,
not as a theorem.

The literature sweep found no ready-made quantitative Douglas--Ando,
Seever, or Baake--Sumner stability theorem that supplies this missing
modulus.  The exact \(\delta=0\) Baake--Sumner normal form anchors the
intuition: exact idempotent Markov structure has equal-input recurrent
classes and no signed shallow web.  What is missing is a signed quantitative
stability version with constants strong enough for the top band.

\subsection{The Remaining Problem}

\begin{openproblem}[Signed quantitative Baake--Sumner stability]
\openbadge
Prove, or refute by exact certificate, the height-conditional web exclusion:
there is a universal \(B<\infty\) and \(\delta_0>0\) such that no exact signed
affine retraction with \(\delta\le\delta_0\) has a hidden top vertex \(v\)
with
\[
  \boxed{\widetilde\sigma_v>\tau\quad\text{and}\quad H>B\tau .}
\]
Equivalently, the \(\widetilde\sigma_v\le\tau\) branch is proved, low-height
shallow faces are real, and HLC is reduced to excluding height-\(\tau\) webs.
\end{openproblem}
