\section{Numerics Record}\label{sec:numerics-record}

This section records what the numerical campaigns actually verified.  It is not
a proof section.  The ambient object is the exact signed affine retraction
\(P\), with \(P\one=\one\) and \(P^2=P\); \(\delta=\max_i\nu_i\),
\(\tau=\sqrt{\delta}\), \(\rho=4\tau\), and \(\kappa=\tau/4\).  The set \(\W\)
contains the \((\rho,\kappa)\)-well-exposed rows, \(C_W=\conv(\W)\), and
\(H=\max_i\distone(p_i,C_W)\).

The final branch variable is geometric.  Throughout this section
\(\sigtilde\) means positive coefficient mass from the hidden top row onto
rows outside \(C_W\), with an \(\varepsilon\)-halo convention when a numerical
distance test is used: rows inside the halo are automatically
\((H-\varepsilon)\)-deep for the canonical deficit \(g_i=H-\phi(p_i)\).  The
formal off-own-site mass \(\sigoff\) is a different quantity.

\begin{warning}\numbadge No entry in this section is a theorem.  Tables below summarize
verified computations, gates, and later scope corrections; finite-corner
constants are not asymptotic claims.
\end{warning}

\subsection{Verification Gates}

A reported \(\W\) was accepted only after robust vertex and exposedness gates:
multiplicities were geometric coincidences, vertices used the corrected routine,
LPs ran with presolve off, and \(\tau\) was recomputed from verified
\(\delta\).  Exact constructions checked \(P\one=\one\), \(P^2=P\), and often
\(P=\Lambda\framemat\), \(\framemat\Lambda=I\); dual runs also required optimal
LP status and small primal/dual residuals.

\begin{numericalresult}[Campaign inventory]
\numbadge The ledger records more than \(67{,}000\) exact verified instances
across independent campaigns, with no exact counterexample found.  This is
evidence only: it supports the current residual formulation but does not prove
HLC or the classical stability problem.
\end{numericalresult}

\subsection{Campaign Ledger}

\paragraph{Campaign nickname glossary.}
\begin{description}[leftmargin=1.1in,style=nextline]
\item[MRP] Middle-regime pinch: the day-1 residual tested by d8.
\item[Financier] The binding far blocker whose deficit pays for the apex poke;
``frame-financing'' means this role is realized by frame-group rows.
\item[pin/neg/epi] The three d9 min-neg dual row families: pinned rows,
negative-mass rows, and exposed epigraph rows.
\item[Budget line] The family law \(g_f=H=2\delta\).
\item[Flat floor] The measured finite-corner ratio
\(\delta/H^2\approx3.49\), now treated as corner-scale only.
\end{description}

\begin{warning}
\numbadge The following table is a numerical inventory, not a theorem list.
The status column follows the report ledger, with post-design corrections
applied where the ledger predates the swarm.
\end{warning}

\begin{center}
\small
\begin{tabular}{@{}p{0.13\textwidth}p{0.26\textwidth}p{0.42\textwidth}p{0.10\textwidth}@{}}
\toprule
Campaign & Verification gate & Numerical outcome & Status \\
\midrule
d8 MRP decider &
\texttt{d8\_mrp3.verify}; corrected \(\W\); presolve off; honest \(\tau\) &
No MRP refutation.  Global minimum \(\delta/H^2=3.4843\) at
\(H/\tau=0.5357\), the finite corner. &
\numbadge \\
d8 historical \(\widetilde\sigma\) wall &
Same d8 gate over the source sweep parameter and \(k\)-group variants &
Tested family followed \(H/\tau\approx\min(\widetilde\sigma,0.536)\);
\(k\)-groups did not move the floor to four digits. &
\numbadge \\
d9 dual certificates &
Gurobi dual simplex, presolve off, all edge LPs optimal; honest
\(\tau\), robust distances &
Budget and wall cells used the same level functional.  Binding blockers were
financing and frame-group rows; final min-neg dual mass sat on pin/neg/epi
families, not frame freedom. &
\numbadge \\
d10 certificate mining &
Verified d8 instances; separator and exposedness LPs with presolve off &
Far top-band mass was robustly present:
\(M_{\mathrm{far}}\in[2.045,2.141]\), so the literal claim
\(T_{\mathrm{far}}=\emptyset\) is false.  The measured financier law
\(\delta_{\min}=g_f/2\) with \(g_f=H\) was later reinterpreted by d11. &
\numbadge, \downgradedbadge \\
d11 scale sweep &
Seven verified scales over \(2.06\) decades; aggregate coupling minimized over
family realization freedom &
The d8 family lies rigidly on \(g_f=H=2\delta\).  It is a budget-line carrier,
not a small-\(\delta\) flat-floor carrier.  The aggregate coupling check gave
\(\min M/\tau\ge1.075\) in the probed wall instance. &
\numbadge \\
d12 depth profiles &
Twelve off-edge stacking instances; HiGHS presolve off; residuals
\(\le3\cdot10^{-16}\); robust \(\W\) &
All exposedness witnesses found were deep with observed \(m_*=1\), and no
all-shallow witness was found.  Scope is corner/budget only; d12 measured an
index-based proxy for \(\sigtilde\), not the final geometric test. &
\numbadge, \downgradedbadge \\
d13 small-\(\delta\) probe &
Three independent generators; band-gated achieved \(\delta\); presolve off;
about \(5000\) verified exact idempotents per target &
Final verdict outcome (c): no hidden-top-vertex floor for
\(\delta\le10^{-2}\).  Best hidden-vertex heights track \(H\approx2\delta\),
not \(0.536\sqrt\delta\). &
\numbadge \\
\bottomrule
\end{tabular}
\end{center}

\subsection{Inline Reproducibility Appendix}

\begin{warning}
\numbadge These local artifacts and certificate extracts are report inputs for
the numerical record; they identify committed files by SHA-256.
\end{warning}

\begin{center}
\tiny
\begin{tabular}{@{}p{0.31\textwidth}p{0.57\textwidth}@{}}
\toprule
Artifact under \texttt{experiments/out/} & SHA-256 \\
\midrule
\texttt{d8\_decision.json} & \texttt{99de674015ccd911d56e63525df3fe0c309607c0bf984fd784e8b73b3e7de6bc} \\
\texttt{d8\_controls.json} & \texttt{e67a0ce976063b3d001307a6f4e95049f3be561cc6775c0f995a4e396b7188c1} \\
\texttt{d12\_dmfprobe.json} & \texttt{dfc41beae6c5dd3b09c85d91107f4032b3a9931e69f8a6adc25ded86f7044283} \\
\texttt{d13\_smalldelta.json} & \texttt{f3bfb374ee4b8a3138b3c526aaaeccf0cb7acf517d4fa99807bd0eee08bd8e18} \\
\texttt{d13\_logs/d5e-02.json} & \texttt{b065583b670274029a5779fbba9b159a04156c3e97fc1223d0934339238bd7e7} \\
\bottomrule
\end{tabular}
\end{center}

\begin{center}
\small
\begin{tabular}{@{}rrrr@{}}
\toprule
\(\delta\) & best hidden-vertex \(H/\tau\) & \(\delta/H^2\) & d13 outcome \\
\midrule
\(5\cdot10^{-2}\) & \(0.447\) & \(5.0\) & anchor deep \\
\(10^{-2}\) & \(0.222\) & \(20.4\) & no floor vertex \\
\(3\cdot10^{-3}\) & \(0.110\) & \(83.3\) & no floor vertex \\
\(10^{-3}\) & \(0.077\) & \(167.6\) & no floor vertex \\
\(3\cdot10^{-4}\) & \(0.035\) & \(833\) & no floor vertex \\
\bottomrule
\end{tabular}
\end{center}

\numbadge Certificate extracts: d8 records the corner cell
\(\delta=0.07175\), \(H/\tau=0.535724\), \(\delta/H^2=3.48432\).
d12 records \(12\) passing depth-profile instances with minimum observed
\(m_*=1\) and no all-shallow witness in its corner/budget scope.  The d13
anchor at \(\delta=5\cdot10^{-2}\) has residuals
\(\|P^2-P\|=0\), identity residual \(4\cdot10^{-16}\), mass-balance residual
\(0\), \(\sigtilde=0\), and shallow fraction \(0\).

\subsection{Post-Design Corrections}

\begin{remark}[Geometric carrier convention]
\modauditbadge The d12 line ``\(\sigtilde=0\)'' is retained only with its
scope correction.  Its code checked positive mass on indices not in \(\W\).
The final convention is geometric distance to \(C_W\); a future nonzero
\(\sigtilde\) claim must use a \(\distone(\cdot,C_W)\) test, with halo rows
counted as deep slack rather than as shallow carriers.
\end{remark}

\begin{remark}[Small-\(\sigtilde\) branch]
\provedbadge The post-design swarm proved the branch
\(\sigtilde\le\tau\): for a hidden top vertex,
\[
  H\le 2(1+2\delta)\max(\sigtilde,\nu_v).
\]
Thus, when \(\delta\le1/4\), \(\sigtilde\le\tau\) gives \(H\le3\tau\) and
directly \(\delta\ge H^2/9\).  In DMF language this branch has existential
deep mass \(m_*=1\) with depth width constant \(C_D=3\).
\end{remark}

\begin{remark}[All-shallow faces]
\modauditbadge An exact rational \(5\times5\) construction after d12 has
\(\sigtilde>0\) and an all-shallow optimal exposedness face.  It lives at
\(H=O(\delta)\), with \(H/\tau\to0\), so it does not refute DMF with
\(O(\delta/\tau)\) depth slack.  It makes the web exclusion height-conditional:
shallow optimal faces exist, but height comparable to \(\tau\) remains open.
\end{remark}

\begin{remark}[Pushed-witness death certificate]
\provedbadge LP support cleanup cannot close the remaining branch.  Pushing a
shallow optimal witness through \(P\) changes the dual cost to
\((B+N)/M_F\), where \(N\) is negative leakage and \(M_F\le1+N\).  Optimality
would require \(M_F\ge1+N/B\), impossible for \(N>0\) when \(B=t^*(v)>0\) and
\(B<\kappa<1\); when \(t^*(v)=0\), exchange handles the case without division
by \(B\).  The surviving problem is not another exposedness-dual algebra trick.
\end{remark}

\begin{remark}[Empirical reframing]
\numbadge The final d13 verdict is outcome (c): for
\(\delta\le10^{-2}\) no verified hidden-top-vertex floor instance was found.
Every verified instance in the full record satisfies the linear pattern
\(H\lesssim2\delta\); the old square-root floor is a corner extrapolation.
\end{remark}

\begin{openproblem}[Linear-law proof target]
\openbadge The proof target is now the linear law \(\delta\ge cH\) for exact
signed affine retractions, equivalently the height-conditional exclusion of
\(\sigtilde>\tau\) shallow webs, and still asks for a signed quantitative
Baake--Sumner stability modulus at positive \(\delta\).
\end{openproblem}
The final numerical verdict is narrow: no exact counterexample was found, and the record supports the linear law, but HLC and the linear law are not proved.
