\section{Refutations and Dead Routes}
\label{sec:refutations-dead-routes}

This section is a guardrail.  A dead route is a proof strategy whose failure is
documented well enough that future work should not restart it without a new idea.  A
downgrade is a statement that was useful during the campaign but whose original
quantifiers or interpretation were later narrowed.  The statuses below are copied from
the ledger, except for the explicitly marked post-design swarm addendum.

Throughout, \(P\) is the exact signed affine retraction, \(p_i\) is its \(i\)-th row,
\(\W\) is the set of \((\rho,\kappa)\)-well-exposed row vertices, and
\(C_W=\conv(\W)\).  The hidden height is
\[
  H=\max_i \distone(p_i,C_W).
\]
For a height-maximizing hidden row vertex \(v\), the canonical separator is the
\(\ell^\infty\)-normalized affine functional \(\phi\) with
\(\phi\le0\) on \(C_W\), \(\sup_{x\in C_W}\phi(x)=0\), and
\(\phi(p_v)=H\).  The deficit vector is
\(g_i=H-\phi(p_i)\); the top band means rows
with small deficit relative to \(H\) or to the oscillation \(\Omega_g\).  A failed
exposedness witness is an optimal dual certificate for \(t^*(v)<\kappa\).  Deep-witness
mass forcing, abbreviated DMF, asks for an optimal witness that places a fixed amount of
mass on rows with deficit near \(H\); an all-shallow witness avoids such rows.

\subsection{Refuted Statements}

\begin{refutedstatement}[Literal psi-gap]
\refutedbadge The literal psi-gap route is false.  In its unconditioned form, far
non-\(S\)-full rows can trade \(S\)-deficit against the \(\lambda\phi\) term.  The
following exact-rational \(6\times6\) idempotent gives a self-contained
counterexample to the bare lemma:
\[
\begin{pmatrix}
1&0&0&0&0&0\\
0&1&0&0&0&0\\
0&0&1&0&0&0\\
0&0&0&1&0&0\\
1/2&1/2&1/16&-1/16&0&0\\
29/32&0&5/32&-1/16&0&0
\end{pmatrix}.
\]
It has \(\delta=1/16\), hence \(\rho=1\), \(\kappa=1/16\).  With
\(S=\{1,2\}\), \(\phi(x)=-2x_4\), \(\psi=x_1+x_2-x_4\),
\(v^*=p_5\), and \(q=p_6\), one has
\(q(S)=29/32<15/16\), \(\|p_5-p_6\|_1=1\), but
\[
  \psi(p_5)-\psi(p_6)=3/32
  <(1/16)(33/16)=\kappa(\max_i\psi(p_i)-\min_i\psi(p_i)).
\]
This refutes only the unconditioned psi-gap input; the canonical-\(\W\)
replacement is the scoped mod-audit route below.
\end{refutedstatement}

The surviving replacement is narrower.  The canonical-\(\W\) conditioned version uses
the canonical top separator after \(\W\) is known and assumes the high-danger-band rows
are \(S\)-full.  Its ledger status is \(\modauditbadge\): it reroutes the old psi
strategy through the top-band residual rather than closing that residual.

\begin{refutedstatement}[General-row leakage]
\refutedbadge The leakage lemma does not hold for arbitrary rows.  The surviving L5'
statement is only the global-height-maximizer version, with ledger status
\(\modauditbadge\).  In particular, a proof may not run a leakage descent from an
unselected hidden row and then appeal to L5' unchanged.
\end{refutedstatement}

\begin{numericalresult}[Literal far-top-band emptiness]
\numbadge The literal statement \(T_{\mathrm{far}}=\emptyset\) is numerically false in
the d10 certificate mining.  Across the tested grid, the far top-band positive feed
stayed bounded, approximately \(M_{\mathrm{far}}\in[2.045,2.141]\), and the far top band
was robustly occupied.  The result is numerical evidence only; the analytic target is an
\(H^2\)-payment or depth statement, not emptiness.
\end{numericalresult}

\subsection{Downgrades}

\begin{downgradedstatement}[Sigma]
\downgradedbadge Older notes used one overloaded external-mass symbol.  The report must
distinguish the formal off-own-site mass \(\sigoff\) from \(\sigtilde\), the positive
coefficient mass on rows outside \(C_W\).  Post-swarm convention makes \(\sigtilde\) geometric:
rows in an \(\varepsilon\)-halo of \(C_W\) are treated as inside the halo, and the halo
error becomes depth slack because such rows are automatically \(H-\varepsilon\)-deep.
\end{downgradedstatement}

\begin{downgradedstatement}[Corner scope]
\downgradedbadge The corner constants
\(\tau_*=2-\sqrt3\), \(2(2-\sqrt3)\), and \((7+4\sqrt3)/4\) explain the measured
finite-corner family, but they do not prove the asymptotic HLC.  The finite-corner
calibration was retracted after the \(\Omega_g\)-handling bug: the corrected DMF chain is
asymptotic, while the numerical corner is a finite point of the tested family.
\end{downgradedstatement}

\begin{downgradedstatement}[D12 scope]
\downgradedbadge D12 remains useful numerical evidence, but its scope is downgraded.
It found twelve verified instances whose optimal witnesses were entirely deep, with
\(\sigoff\) about \(1.01\) to \(1.07\) but measured index-not-in-\(\W\) carrier mass zero.  The
post-w9 and swarm audits reinterpret this as corner-regime evidence: d12 measured an
index-based proxy, and it did not profile a verified small-\(\delta\) web instance.
\end{downgradedstatement}

\begin{downgradedstatement}[All-shallow faces]
\downgradedbadge The absolute hope that all-shallow optimal faces do not exist is too
strong.  The post-design s5 refuter gives an exact \(5\times5\) rational certificate
with hidden \(v\), \(\sigtilde>0\), and an optimal witness supported on a far row with
deficit \(g=0\).  The certificate is exact-rational with mod-audit status and lives only
at height \(H=O(\delta)\).  Therefore the web exclusion must be height-conditional; this
example does not refute DMF with \(E(\delta)=O(\delta/\tau)\).
\end{downgradedstatement}

The L2' recursion warning belongs in the same category.  L2' gives a
\(\rho\)-shadow with status \(\modauditbadge\), but the recursive proof idea built on it
is gapped at the target scale.  Likewise, top-vertex reduction is allowed for HLC, while
non-top hidden vertices are not interchangeable with height-maximizing ones.

\subsection{Dead Proof Routes}

The canonical-\(g\) kernel-energy route has ledger status DEAD ROUTE: the source
anti-lemma bounds its own positive quadratic energy by \(\delta\Omega_g^2\), too small
to force Branch A.  The pure vertical functional \(g/\Omega_g\) is a source-note warning,
not a standalone ledger result.  It explains why the wall constant is near \(1/2\), but
it overshoots the top-band obstruction and cannot by itself expose \(v\).

Row exactness at the financing blocker has ledger status DEAD ROUTE: it contains no
\(H\) or \(\sigtilde\).  Diagonal or column exactness at the blocker is likewise vacuous
or \(H\)-free in the relevant regimes.  These no-gain statements are useful diagnostics,
not closure lemmas.  The NG' stronger consistency reading is retracted; only the
dead-route guidance survives.

\begin{refutedstatement}[Raw factorization gauge route]
\refutedbadge A raw \(\framemat\Lambda=I\) argument is not gauge-invariant.  Under
changes of realization, the invariant content is row exactness and column exactness for
\(P^2=P\), not a preferred frame coordinate.  The raw factorization route is therefore
recorded as dead-route/refuted guidance.
\end{refutedstatement}

\begin{downgradedstatement}[LP support-cleanup route]
\provedbadge The post-design pushed-witness calculation gives a death certificate for
support-cleanup as a proof of the remaining branch.  If shallow witness rows are pushed
through \(P\), negative leakage changes the objective from \(B\) to \((B+N)/M_F\).  When
\(B=t^*(v)>0\), remaining optimal would require \(M_F\ge 1+N/B\), while the available
bound is \(M_F\le 1+N\) and \(B<\kappa<1\).  Any \(N>0\) breaks the argument.  The
\(t^*(v)=0\) case is handled by the exchange identity without dividing by \(B\).
\end{downgradedstatement}

Route dictionary for the table: a high zero face is a low-deficit face where
dual slack can concentrate; raw circuit bounds are unsigned combinatorial
cycle estimates on coefficient support; the KKT localization-energy dichotomy
is the failed attempt to split exposedness optimality into a local KKT case and
an energy-payment case; a log-staircase is a chain of shells with geometrically
changing heights.

\begin{longtable}{p{0.24\linewidth}p{0.20\linewidth}p{0.42\linewidth}}
\toprule
Route & Ledger status & Failure mode \\
\midrule
Literal psi-gap route & REFUTED & Exact-rational and independent counterexamples; only the conditioned canonical-\(\W\) form remains. \\
Top-band localization as \(T_{\mathrm{far}}=\emptyset\) & REFUTED / NUMERICAL & D10 shows bounded but nonzero far top-band occupancy. \\
Canonical-\(g\) kernel energy & DEAD ROUTE & Its own energy bound is too small to force the needed height payment. \\
Row exactness at financier & DEAD ROUTE & Gives an inequality with no \(H\) or \(\sigtilde\). \\
Diagonal exactness at blocker & DEAD ROUTE & NG' demystifies it as vacuous or \(H\)-free. \\
Raw factorization gauge route & DEAD ROUTE / REFUTED & Gauge choices add no invariant content beyond \(P^2=P\). \\
Finite-corner equals asymptotic proof & RETRACTED/\newline DOWNGRADED & Exact finite constants are not an HLC proof at small \(\delta\). \\
Broad d12 DMF proof & RETRACTED/\newline DOWNGRADED & Evidence applies to profiled corner/budget regimes, not the small-\(\delta\) web case. \\
Averaging or quasi-stationary potentials & DEAD ROUTE & The gain is \(O(\delta)\), the same scale as the slop. \\
Projection-norm height tests & DEAD ROUTE & Re-derive weak bounds only. \\
Raw circuit bounds & DEAD ROUTE & Do not close the exposed-hull/HLC gap. \\
Unlocalized dual descent & DEAD ROUTE & Loses a constant much larger than the target height. \\
Maximality contradictions without localization & DEAD ROUTE & Do not control the high zero face. \\
Rank induction via stochastic complement & DEAD ROUTE & Parked for this route despite rank-preservation tools. \\
KKT localization-energy dichotomy & DEAD ROUTE & Leaves the same energy-route orphans. \\
Pure convex shadow composition & DEAD ROUTE & Becomes vacuous as the mixing parameter tends to \(1\). \\
Log-staircase or shell route & DEAD ROUTE & Exactness and the one-mode wall kill the common pattern; no counterexample was produced. \\
\bottomrule
\end{longtable}

\subsection{What Remains Open}

\begin{proposition}[Small-\(\sigtilde\) branch]
\provedbadge In the post-design s8 addendum, if geometric \(\sigtilde\le\tau\) and
\(\delta\le1/4\), then
\[
  H\le 2(1+2\delta)\max(\sigtilde,\nu_v)\le 3\tau .
\]
Consequently \(\delta\ge H^2/9\) directly, and existential DMF holds on this branch with
\(m_*=1\) and \(C_D=3\).  This branch no longer belongs to the open problem.
\end{proposition}

\begin{numericalresult}[Empirical reframing]
\numbadge The verified record no longer contains a banked small-\(\delta\) flat floor.
The sw11/sw12 forensics report no verified flat-floor instance below about
\(\delta=0.06\), and final d13 gives outcome (c): every verified instance in the record
satisfies the linear behavior \(H\lesssim 2\delta\).  The linear law is the empirical
truth of the campaign record, not yet a theorem.
\end{numericalresult}

\begin{openproblem}[Height-conditioned shallow-web exclusion]
\openbadge The final open is height-conditioned.  With \(\sigtilde\) interpreted
geometrically, HLC is equivalent, in the post-swarm synthesis, to excluding a hidden top
vertex with
\[
  \sigtilde>\tau
  \qquad\text{and}\qquad
  H>B\tau
\]
for a universal constant \(B\).  This is the signed quantitative Baake--Sumner stability
problem for shallow hidden top-band webs.  The exact \(\delta=0\) anchor is banked, but
the perturbative signed statement is still open.
\end{openproblem}

Future proof work should attack that last web-stability problem directly.  The routes
listed above either fail outright, prove only a scoped replacement, or explain the
finite-corner/budget record without excluding high shallow webs.
