\section{Multi-Agent Methodology And Audit Catches}

\subsection{Method Contract}

This report records an exploration lane, not a banked final proof.  The
orchestrator was the agent maintaining the live state, delegation log, and
status ledger.  A worker was an independent model run assigned one narrow
lane: proof search, counterexample search, numerical verification, or hostile
review.  The Fable closer was the large-context synthesis pass that compressed
the late campaign around the exposedness-dual witness, meaning the LP dual
certificate for failed exposedness, and the deep-witness mass forcing
obstruction, abbreviated DMF: the demand that an optimal witness put definite
mass near hidden height $H$.

The done bar used during the campaign was intentionally stricter than ordinary
drafting.  A claimed proof needed two-family audit: at least one Claude-family
and one Codex-family derivation, with an adversarial pass by a party other than
the author.  A claimed counterexample needed an exact rational family and a
verification script checking $P\one=\one$, $P^2=P$, the row negative-mass bound
$\delta$, and the distance lower bound.  An honest stall was also an acceptable
terminal state, but only after all surviving lanes were named as precise
obstructions.

A derive-first hostile review means that the reviewer re-derives the statement
from the definitions before trusting the submitted proof.  This mattered in
several places: the reviewer was asked to find the hidden quantifier, sign, or
normalization error rather than to edit prose.  A red-green check means that a
script or certificate first exposed a failure mode, and then the corrected gate
was rerun so that the same failure would be caught in the future.

The method was deliberately local.  The notes under this exploration lane are
provenance for this report; promotion to the main project requires a separate
banking phase.  Local-only provenance therefore has two consequences for the
reader.  First, badges below describe the audited state of this lane.  Second,
external literature and main-project imports are used only where byte-grounded
or explicitly allowed by the ledger.

\subsection{Ledger Discipline}

Status tags are methodological, not cosmetic.  A badge controls what kind of
sentence may be written.  \provedbadge{} means that a proof survived the stated
audit.  \modauditbadge{} means that the proof exists but its correction,
hypothesis, or banking caveat must travel with it.  \numbadge{} means verified
computation, never a theorem.  \openbadge{} means the report is naming work
still to be done.  \refutedbadge{} and \downgradedbadge{} prevent an old route
from being silently resurrected.

This discipline also explains the notation policy.  The old notes overloaded
the external-mass symbol.  The report distinguishes the formal off-own-site
mass $\sigoff$ from the geometric non-$\conv(\W)$ mass $\sigtilde$, where
$\W$ is the set of well-exposed row vertices.  In the final convention,
$\sigtilde$ is geometric: it is measured by positive carrier mass at positive
$\ell^1$ distance from $C_W=\conv(\W)$, with any $\varepsilon$-halo counted as
depth slack.  Thus an index not belonging to $\W$ is only a proxy unless its
row is also geometrically outside $C_W$.

\begin{warning}
\downgradedbadge{} Older $\sigoff$-resolved claims are not automatically
$\sigtilde$-claims.  In particular, the d12 probe measured an index-based
proxy in the profiled instances.  Those data remain useful for that family,
but they do not settle the geometric web case.
\end{warning}

The same rule applies to constants.  Finite-corner constants describe the
verified corner family and may not be presented as asymptotic constants for
the hidden localization claim (HLC), the desired bound $\delta\ge aH^2$.
Conversely, an asymptotic statement such as HLC may use the corner as evidence
or calibration only after its status has been downgraded to numerical or
mod-audit evidence.

\subsection{Audit Catches}

The campaign's main value is not that many agents agreed.  Agreement is only
evidence when the agents failed independently at the same sharply described
object and when stronger statements were downgraded rather than defended.
Four catches changed the shape of the final open problem.

\begin{refutedstatement}
\refutedbadge{} The literal psi-gap route is false.  The proposed uniform gap
for $\rho$-far non-$S$-full rows has exact-rational counterexamples, so the
original F-psi route is not a usable theorem.  Only the conditioned
canonical-$\W$ replacement may be cited, and even that reroutes through the
same top-band residual.
\end{refutedstatement}

\begin{downgradedstatement}
\downgradedbadge{} The NG' consistency lemma was downgraded.  Its useful
content is dead-route guidance: row, column, or diagonal exactness at the
financing or blocker row does not by itself contain the missing $H$-scale
information.  It is not a positive consistency theorem closing the web case.
\end{downgradedstatement}

\begin{warning}
\downgradedbadge{} The broad d12 interpretation was narrowed after the
$\sigtilde$ height-collapse audit.  The observed witnesses were deep with
$m_*=1$ in the profiled corner and budget-line regimes, but the small-$\delta$
web case was not measured there.  The final small-$\delta$ d13 probe is
[pending] in this report.
\end{warning}

The post-ledger swarm added two further controls.  First, \modauditbadge{} an
exact rational $5\times5$ construction gives an all-shallow optimal face with
hidden rows and $\sigtilde>0$, but only at height $H=O(\delta)$; it is an
audit-pending height-conditional warning, not a refutation of DMF with
$O(\delta/\tau)$ slack.  Second, \provedbadge{} the branch $\sigtilde\le\tau$
is closed: the height cap
\[
        H\le 2(1+2\delta)\max(\sigtilde,\nu_v)
\]
gives $H\le3\tau$ for $\delta\le1/4$, hence $\delta\ge H^2/9$ directly and
existential DMF holds there with $m_*=1$ and $C_D=3$.

\provedbadge{} The attempted LP support-cleanup route also received a death
certificate.  If one pushes shallow witness rows through $P$, negative leakage
changes the dual objective from $B$ to $(B+N)/M_F$.  Since $M_F\le1+N$ while
optimality would require $M_F\ge1+N/B$ and $B<\kappa<1$, any $N>0$ breaks the
route.  The remaining obstruction is therefore not another exposedness-dual
algebra trick; it is a signed quantitative Baake--Sumner stability problem.

\begin{numericalresult}
\numbadge{} The empirical record was reframed after the sw11/sw12 forensics.
The ``flat floor'' was never verified below about $\delta=0.06$ in the saved
record.  Every verified small-scale instance in the campaign record satisfied
the budget-line behavior $H\lesssim2\delta$, while the d13 final outcome
remains [pending].
\end{numericalresult}

\subsection{Numerical Gates}

The numerical pipeline was treated as certificate generation, not as proof.
The recurring gates were exact or high-precision checks of $P\one=\one$ and
$P^2=P$, honest use of $\tau=\sqrt{\delta}$, presolve-off LP verification when
dual certificates mattered, multiplicity-correct tests for $\W$, and residual
checks at the scale advertised by the source note.  Numerical claims were
allowed to shape conjectures, expose false routes, and select constants for
inspection.  They were not allowed to become theorem statements.

This is why red-green checks appear repeatedly in the notes.  LP presolve
artifacts, vertex-multiplicity bugs, scale degeneracies, and the geometric
$\sigtilde$ proxy each produced a concrete correction.  The report keeps those
corrections in the text because they are part of the mathematical provenance:
without them, a reader would not know which tempting shortcuts have already
failed.

\subsection{Compact Timeline}

\begin{itemize}[leftmargin=*]
\item Day 1 built the signed-idempotent working model, the exposed-hull/HLC
reduction, the audited belt of local lemmas, and the first numerical floor and
wall record.  The end-of-day state still used the historical $\sigoff$-style
wall language and left Branch A, Branch B, and the psi-gap route open.
\item Day 2 compressed those branches through the Fable closer and hostile
Codex audits.  The dual identity, exchange bound, row-witness mechanism, and
corner constants were separated into proved, mod-audit, and numerical parts.
The literal psi-gap and NG' routes were removed from the proof path.
\item The d12 and wave-9 passes replaced broad witness-depth optimism with a
geometric $\sigtilde$ dichotomy.  The $\sigtilde$-small branch gives height
collapse, while the $\sigtilde$-large branch is the shallow hidden-web case.
\item The nine-agent DMF swarm sharpened the residual: low-height all-shallow
faces exist, the $\sigtilde\le\tau$ branch is proved, and LP witness-pushing
cannot close the remaining branch.  The sw11/sw12 forensics then reframed the
empirical target as the possible linear law $H=O(\delta)$, with final d13
confirmation still [pending].
\end{itemize}

\subsection{What Remains Methodologically Open}

\begin{openproblem}
\openbadge{} The final open form is height-conditional web exclusion: rule out
a hidden top vertex with geometric $\sigtilde>\tau$ at height $H>B\tau$, for a
universal $B$.  Equivalently for this report's route, prove the signed
quantitative Baake--Sumner stability statement needed to exclude a
self-sustaining shallow hidden top-band web, where the top band consists of
rows with small separator deficit.  The $\delta=0$ Baake--Sumner anchor is
byte-pinned, but the dimension-free perturbative modulus is still open.
\end{openproblem}

Future proof writers should therefore attack the web exclusion or the stronger
linear law directly.  The dead routes are already informative: the literal
psi-gap, raw factorization gauge arguments, unlocalized witness descent,
financier-row exactness, blocker diagonal exactness, and finite-corner
calibration do not close HLC.  Independent convergence on this residual is
useful evidence that the obstruction map is honest; it is not a substitute for
the missing stability theorem.
