\documentclass[11pt]{article}
\usepackage[margin=1.15in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{xcolor}
\usepackage{hyperref}
\hypersetup{colorlinks=true,linkcolor=blue!55!black,urlcolor=blue!55!black}

\theoremstyle{plain}
\newtheorem{conjecture}{Conjecture}
\newtheorem{theorem}{Theorem}
\newtheorem{proposition}[theorem]{Proposition}
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\theoremstyle{remark}
\newtheorem{remark}{Remark}

\newcommand{\one}{\mathbf 1}
\newcommand{\R}{\mathbb R}
\newcommand{\dist}{\operatorname{dist}_1}
\newcommand{\conv}{\operatorname{conv}}
\newcommand{\negm}{\operatorname{neg}}
\newcommand{\W}{\mathcal W}
\newcommand{\sigt}{\widetilde{\sigma}}

\title{The Kernel Conjecture:\\ a self-contained statement of the single open input\\
to the dimension-free classical stability theorem}
\author{Classical-portfolio campaign (exploration lane)}
\date{11 June 2026}

\begin{document}
\maketitle

\noindent\textbf{Purpose.} This document states, with every definition included and no
reliance on any campaign artifact, the \emph{minimal conjecture} whose proof would complete
the full chain
\[
\textbf{Kernel Conjecture}
\;\Longrightarrow\; \text{linear hull bound}
\;\Longrightarrow\; \text{HLC}
\;\Longrightarrow\; \text{\texttt{op-exposed-hull}}
\;\Longrightarrow\; \text{\texttt{op-classical}},
\]
where every implication arrow is already proved (or proved modulo recorded audits) in the
campaign record. A reader needs only basic linear algebra and the vocabulary of stochastic
matrices. Section~\ref{sec:chain} states precisely what the conjecture buys; Section~%
\ref{sec:stronger} records the stronger ``working form'' used by the current proof attack;
Section~\ref{sec:evidence} lists the evidence and the constraints any proof or refutation
must respect.

\section{Setting}

\begin{definition}[Exact signed idempotent]\label{def:esi}
Let $n\in\mathbb N$. A matrix $P\in\R^{n\times n}$ is an \emph{exact signed idempotent} if
\[
P\one=\one \qquad\text{and}\qquad P^2=P ,
\]
where $\one=(1,\dots,1)^{\mathsf T}$. Its \emph{negativity} is
\[
\delta(P)\;:=\;\max_{1\le i\le n}\ \sum_{j=1}^{n}\max\{-P_{ij},\,0\}
\]
(the largest total negative mass in any single row). A row-stochastic idempotent is exactly
an exact signed idempotent with $\delta(P)=0$.
\end{definition}

\begin{definition}[The three scales]\label{def:scales}
Given $\delta=\delta(P)$, set
\[
\tau:=\sqrt{\delta},\qquad \rho:=4\tau,\qquad \kappa:=\tau/4 .
\]
\end{definition}

\begin{definition}[Row geometry]\label{def:rows}
Write $p_i\in\R^n$ for the $i$-th row of $P$, regarded as a point of $\R^n$ with the
$\ell^1$ metric $\|x-y\|_1=\sum_j|x_j-y_j|$. For a nonempty set $S\subseteq\R^n$ put
$\dist(x,S)=\inf_{s\in\conv S}\|x-s\|_1$, where $\conv$ denotes the convex hull.
\end{definition}

Note each row satisfies $\sum_j p_{ij}=1$ and $\sum_j |p_{ij}|\le 1+2\delta$; all rows lie
in a common affine hyperplane and pairwise $\ell^1$ distances are at most $2+4\delta$.

\begin{definition}[Row vertex, multiplicity-correct]\label{def:vertex}
A row $p_v$ is a \emph{row vertex} of $P$ if
\[
p_v\notin \conv\{\,p_j \;:\; p_j\neq p_v \text{ as vectors of } \R^n\,\}.
\]
(Geometrically coincident duplicate rows count as a single point; a point repeated many
times is still a vertex if it lies outside the hull of the \emph{other} points.)
\end{definition}

\begin{definition}[$(\rho,\kappa)$-exposedness and the visible set $\W$]\label{def:exposed}
Let $p_v$ be a row vertex. An \emph{admissible exposer for $v$} is an affine function
$h:\R^n\to\R$ with
\[
h(p_v)=0
\qquad\text{and}\qquad
0\le h(p_j)\le 1 \quad\text{for every row } p_j .
\]
The \emph{exposedness margin} of $v$ is
\[
t^*(v)\;:=\;\sup_{h \text{ admissible}}\ \ \min\{\,h(p_j)\;:\;\|p_j-p_v\|_1\ge\rho\,\},
\]
with the convention $t^*(v)=+\infty$ when no row is $\ell^1$-distance $\ge\rho$ from $p_v$.
The vertex $v$ is \emph{$(\rho,\kappa)$-exposed} if $t^*(v)\ge\kappa$, and
\emph{hidden} otherwise. The \emph{visible set} is
\[
\W=\W(P):=\{\, v \;:\; p_v \text{ is a } (\rho,\kappa)\text{-exposed row vertex of } P \,\}.
\]
\end{definition}

Informally: an exposed vertex can be linearly separated, with margin at least $\kappa$,
from every row that is genuinely far ($\ge\rho$) from it; rows inside the $\rho$-ball are
exempt. At $\delta=0$ the visible vertices are exactly the distinct rows of the recurrent
(equal-input) blocks of a stochastic idempotent.

\begin{definition}[Height]\label{def:height}
If $\W\neq\emptyset$, the \emph{height} of a row $p_i$ is
$\dist\!\big(p_i,\conv\{p_w:w\in\W\}\big)$, and the height of $P$ is
\[
H=H(P):=\max_{1\le i\le n}\ \dist\!\big(p_i,\ \conv\{p_w : w\in\W\}\big).
\]
Because $\dist(\cdot,\conv\W)$ is convex and every row is a convex combination of the
geometrically distinct row vertices, the maximum is attained at a row vertex; if $H>0$,
any maximising vertex is necessarily hidden. We call such a vertex a \emph{hidden top
vertex}.
\end{definition}

\begin{definition}[Invisible mass $\sigt_v$]\label{def:sigt}
Let $C_{\W}:=\conv\{p_w:w\in\W\}$ and let $p_v$ be a row vertex. The \emph{invisible
(positive) mass} of $v$ is
\[
\sigt_v\;:=\;\sum_{j\,:\,\dist(p_j,\,C_\W)>0}\ \max\{P_{vj},\,0\},
\]
the total positive coefficient mass that row $v$ places on rows lying strictly outside
$C_\W$ --- \emph{including} the index $j=v$ itself when $p_v\notin C_\W$ and $P_{vv}>0$.
\end{definition}

\begin{remark}[Halo robustness]
Replacing the condition $\dist(p_j,C_\W)>0$ by $\dist(p_j,C_\W)>\varepsilon$ changes
$\sigt_v$ only by mass sitting in the $\varepsilon$-halo of $C_\W$; for every statement
below, halo mass can be absorbed as an $\varepsilon$-loss in the height (rows
$\varepsilon$-close to $C_\W$ are, for any $1$-Lipschitz witness of the height, within
$\varepsilon$ of being as deep as $C_\W$ itself). The $\varepsilon=0$ form is used
throughout.
\end{remark}

\section{The Kernel Conjecture}\label{sec:kernel}

\begin{conjecture}[Kernel Conjecture; invisible-mass height bound]\label{conj:kernel}
There exist universal constants $\delta_0>0$ and $B<\infty$ (independent of the dimension
$n$) such that for every $n$ and every exact signed idempotent $P\in\R^{n\times n}$ with
$\delta=\delta(P)\le\delta_0$:
\begin{enumerate}
\item[\textup{(i)}] $\W(P)\neq\emptyset$; and
\item[\textup{(ii)}] every \emph{hidden} row vertex $v$ with
\[
\sigt_v\;>\;\tau\;=\;\sqrt{\delta}
\]
satisfies
\[
\dist\!\big(p_v,\ \conv\{p_w:w\in\W\}\big)\;\le\; B\,\tau .
\]
\end{enumerate}
\end{conjecture}

\begin{remark}[Any constants suffice]
The downstream chain consumes \emph{any} universal pair $(\delta_0,B)$. No specific value
is required; the corner analysis (Section~\ref{sec:evidence}) shows $B$ cannot be taken
below $2(2-\sqrt3)\approx 0.536$ unless the hypothesis class is empty, and the verified
numerical record is consistent with the hypothesis class being empty altogether (no
verified instance with $\sigt_v>\tau$ and height $>0.1\tau$ has ever been produced).
\end{remark}

\begin{remark}[Why the hypothesis $\sigt_v>\tau$ is there, and why this is minimal]
The complementary regime is already a theorem: if $\sigt_v\le\tau$ then (writing
$\nu_v\le\delta$ for $v$'s negative row mass)
\[
\dist(p_v,C_\W)\;\le\;2(1+2\delta)\max\{\sigt_v,\nu_v\}\;\le\;3\tau
\qquad(\delta\le\tfrac14),
\]
by splitting the row identity $p_v=\sum_j P_{vj}p_j$ at $C_\W$: the visible positive mass
has barycentre in $C_\W$, and what remains is at most $\max\{\sigt_v,\nu_v\}$ on either
side. \emph{[s8 height cap; proved in the campaign record, with the earlier
height-collapse form $\sigt_v\le s<1 \Rightarrow H\le \delta(2+4\delta)/(1-s)$.]}
Thus Conjecture~\ref{conj:kernel} is exactly the missing branch, and nothing weaker
completes the dichotomy.
\end{remark}

\section{What the conjecture completes}\label{sec:chain}

\begin{theorem}[Conditional; the full chain]\label{thm:chain}
Assume Conjecture~\ref{conj:kernel} with constants $(\delta_0,B)$, and let
$C_1:=\max\{B,3\}$. Then for every $n$ and every exact signed idempotent $P$ with
$\delta\le\min\{\delta_0,\tfrac14\}$:
\begin{enumerate}
\item[\textup{(a)}] \textbf{(Linear hull bound)} every row of $P$ lies within
$C_1\sqrt{\delta}$ of $\conv\{p_w:w\in\W\}$, i.e.\ $H(P)\le C_1\sqrt\delta$; equivalently
$\delta\ge H^2/C_1^{\,2}$ \textup{(the HLC inequality)}.
\item[\textup{(b)}] \textbf{(Exposed-hull stability, \texttt{op-exposed-hull})} $P$ is
within distance $C_2\sqrt{\delta}$ (max-row-$\ell^1$) of a matrix whose rows all lie in
$\conv\{p_w:w\in\W\}$, with $C_2$ universal.
\item[\textup{(c)}] \textbf{(Classical stability, \texttt{op-classical})} there are
universal $\eta_0,C>0$ such that every row-stochastic $Q$ with
$\|Q^2-Q\|_{\infty\to\infty}\le\eta\le\eta_0$ lies within $C\sqrt{\eta}$
(max-row-$\ell^1$) of an exactly idempotent row-stochastic matrix.
\end{enumerate}
\end{theorem}

\begin{proof}[Assembly (each ingredient proved in the campaign record)]
(a) The height maximum is attained at a row vertex (Definition~\ref{def:height}); if
$H>0$ that vertex is hidden; apply the $\sigt$-dichotomy: the s8 cap when
$\sigt_v\le\tau$, the conjecture when $\sigt_v>\tau$. (b) is the two-family-verified
assembly \emph{op-exposed-hull $\Leftarrow$ HLC} (grand assembly, $C'=\max(4A,1/\sqrt a)$
with $a=1/C_1^{\,2}$ here). (c) is the previously proved cluster theorem
(\texttt{thm-cluster}, summand-count-free assembly) composed with the validated
signed/stochastic equivalence (\texttt{lem-classical-equiv}, explicit universal
constants). Statuses: (a)-assembly and the s8 cap, proved; (b), proved mod recorded
audit; (c), machine-validated (\texttt{af}) plus proved.
\end{proof}

\section{The stronger working form (for attackers)}\label{sec:stronger}

The current proof attack does not target Conjecture~\ref{conj:kernel} directly but a
stronger, more structured statement, recorded here because every proved tool composes
with it. Fix $P$, a hidden top vertex $v$, and a $1$-Lipschitz (w.r.t.\ $\ell^1$) affine
$\varphi$ with $\varphi\le 0$ on $C_\W$, $\sup_{C_\W}\varphi=0$, $\varphi(p_v)=H$
(a \emph{canonical separator}; it exists by $\ell^1$/$\ell^\infty$ duality). The
\emph{deficit} $g_i:=H-\varphi(p_i)$ satisfies $g\ge0$, $g_v=0$, $g=Pg$ (harmonicity:
$\varphi$ is affine and rows reproduce, $p_i=\sum_j P_{ij}p_j$), and
$\Omega:=\max_i g_i-\min_i g_i\le 2+4\delta$. For a threshold $t\in(0,\kappa\Omega]$,
the \emph{shallow band} is $S_t=\{i: g_i<t\}$, the \emph{band block} is
$P_{S_tS_t}$, and the \emph{carrier graph} is the directed graph on $S_t$ with an edge
$i\to j$ when $P_{ij}>0$. For a strongly connected component $\mathcal C$ with directed
diameter $L$, the \emph{path product} is
\[
\Pi_{\mathcal C}\;:=\;\min_{i,j\in\mathcal C}\ \max_{\text{directed paths } i\to j
\text{ in }\mathcal C}\ \prod_{\text{edges } (k,l)} P_{kl}.
\]

\begin{conjecture}[Path-product floor; thin-chain exclusion --- implies
Conjecture~\ref{conj:kernel}]\label{conj:floor}
There are universal $\delta_0,B,c,C'$ such that for $\delta\le\delta_0$: if $v$ is a
hidden top vertex with $\sigt_v>\tau$ and $H>B\tau$, then for some threshold
$t\in[\kappa\Omega/2,\,\kappa\Omega]$, every carrier-graph component $\mathcal C$ of
$S_t$ that carries positive mass of $v$ satisfies
\[
\Pi_{\mathcal C}\;\ge\; c\,\tau \;-\; C' L\,\delta .
\]
\end{conjecture}

\noindent The implication Conjecture~\ref{conj:floor} $\Rightarrow$
Conjecture~\ref{conj:kernel} is the proved \emph{component finisher}: a component whose
path products beat the signed/idempotence error has, by a Birkhoff--Hilbert projective
contraction argument requiring \emph{no spectral gap}, all its rows collapsing to a
near-equal-input cluster; near-equal-input clusters are exposed (audited near-coincidence
machinery), contradicting hiddenness. The wave-12 survivor inequality
$\Pi_{\mathcal C}\le E_L(\delta,\zeta)+2(1+\delta)\varepsilon/(0.85\tau-4\delta)$ makes
the floor above the exact negation of the surviving configuration class. Of the two
sub-issues that rode with this form, one is now closed: \emph{periodicity is excluded}
--- for a closed positive band component, exact idempotence forbids period $d\ge2$
outright ($1\le3\delta+4\delta^2$, a contradiction for $\delta<\tfrac14$; proved and
independently audited, with approximate-closure tolerance
$\eta<1-\sqrt{3\delta+4\delta^2}$). The analytic --- as opposed to measured --- closure
of the band's positive kernel remains open.

\paragraph{The cloning obstruction (status correction to
Conjecture~\ref{conj:floor}).} Splitting an index $r$ into $M$ duplicates via
$\widehat P_{ab}=\alpha_b P_{\pi(a),\pi(b)}$ (fiber weights $\alpha_b>0$ summing to $1$
per fiber) preserves exact idempotence, row sums, $\delta$, and --- as an
$\ell^1$-isometry on row differences under which exposing functionals lift and descend
--- every geometric quantity in this document ($\W$, $H$, $g$, $\sigt_v$, hiddenness,
the high-hidden antecedent), while every raw-index path product through the cloned
fibers decays as $\Pi\le(1+\delta)/M$. Hence Conjecture~\ref{conj:floor} \emph{as
written} (raw-index carrier graph) is refuted by cloning any antecedent-realizing
instance --- and such an instance now exists (item~1 below, certified exact at
$\delta=0.2329$): \textbf{the raw-index floor is refuted outright for any
$\delta_0\ge0.233$}. For small $\delta_0$ (below the corner scale) its status
remains: \emph{true iff the high-hidden antecedent is empty there} --- it carries no
intermediate content beyond Conjecture~\ref{conj:kernel} itself. The
multiplicity-correct replacement is:

\begin{conjecture}[Multiplicity-correct path-product floor]\label{conj:quotient-floor}
Let $i\sim j$ mean $p_i=p_j$ as vectors, and for classes set
\[
\overline P_{[i],[j]}:=\sum_{b\in[j]}P_{ib}.
\]
For $S_t=\{i:g_i<t\}$, let $\overline{\mathcal G}_t$ be the directed graph on
classes $[i]\subset S_t$ with edge $[i]\to[j]$ when
$\overline P_{[i],[j]}>0$. For a strongly connected component
$\overline{\mathcal C}$, define $\overline\Pi_{\overline{\mathcal C}}$
by the same min--max path-product formula using the edge weights
$\overline P$.

There are universal $\delta_0,B,c,C'$ such that, for
$\delta\le\delta_0$, if $v$ is a hidden top vertex with
$\sigt_v>\tau$ and $H>B\tau$, then for some
$t\in[\kappa\Omega/2,\kappa\Omega]$, every quotient carrier component
$\overline{\mathcal C}$ of $S_t$ carrying positive $\overline P$-mass
from $[v]$ satisfies
\[
\overline\Pi_{\overline{\mathcal C}}
\ge c\tau-C'\overline L\,\delta .
\]
\end{conjecture}

\noindent Facts secured for this form (wave 16, audited statements in the dossier):
the quotient weights are clone-invariant by construction; the quotient matrix
$\overline P$ is itself exactly idempotent and stochastic with
$\delta(\overline P)\le\delta(P)$, the deficit $g$ descends harmonically, band closure
descends, and the component finisher reattaches (class collapse equals index collapse,
modulo one flagged residual: internal signed cancellation inside a duplicate class).
Two caveats discovered with it: exact quotienting is \emph{not} conjugation-robust
(a similarity $S=I+O(\eta)$ smears duplicates into an $\eta$-cloud; the robust target
is the $\eta_{\mathrm{cl}}$-clustered quotient with
$\eta_{\mathrm{cl}}\lesssim\delta$), and two independent prover routes die at the same
missing \emph{anti-splitting principle}: high hidden height provably forces aggregate
shallow off-$C_{\W}$ carrier mass $\ge(B/3-4)\tau$, but pinning a $c\tau$ share into
\emph{one} closed quotient component needs a dimension-free bound on the number of
geometrically distinct shallow classes hit by $P_v^+$ --- which no audited tool
supplies.

\section{Evidence, constraints, and failure maps}\label{sec:evidence}

Any resolution of Conjecture~\ref{conj:kernel} must respect all of the following, each
verified or proved in the campaign record (branch \texttt{agent-a/classical-portfolio},
dossier \texttt{notes/wave5-sigma-wall-parallel.md}, worker verdicts
\texttt{notes/swarm-answers/}):

\begin{enumerate}
\item \textbf{Empirical record.} $67{,}000$+ verified exact instances over six
independent campaigns (d1--d14), all scales $\delta\in[6\times10^{-4},0.25]$: every
instance satisfies the \emph{linear law} $\delta\gtrsim H/2$. Two dedicated
counterexample agents with distinct template families (chains, trees, frame-chains,
parallel bundles, periodic components) failed against full verification gates, with
recorded per-template failure displays. \emph{Above-corner correction (2026-06-11):}
the high-hidden antecedent IS realizable above the corner scale --- an exact rational
instance ($n=10$, $k=5$, $\delta=0.2329$, independently certified, hiddenness decided
exactly) has a hidden top vertex with $\sigt_v>\tau$ \emph{and} $H/\tau=0.1002$ (a
second robust instance at $H/\tau=0.1000$). Both satisfy the linear law ($H\le2\delta$).
\textbf{Below the corner scale $\delta^*=(2-\sqrt3)^2\approx0.0718$ the antecedent
remains un-entered} (d13: max $H/\tau$ over hidden vertices collapses $\sim2\delta/\tau$
as $\delta\to0$) --- the emptiness question, and with it the content of both floor
conjectures, lives entirely in the small-$\delta$ regime.
\item \textbf{The corner.} The historically measured ``wall'' $H/\tau=0.536$ and
``floor'' $\delta/H^2=3.48$ are the finite-$\delta$ corner $\tau^*=2-\sqrt3$,
$H/\tau=2(2-\sqrt3)$, $\delta/H^2=(7+4\sqrt3)/4$ (exact closed forms, two-family
confirmed); the corner instance itself has $\sigt_v=0$, i.e.\ lies in the
\emph{proved} branch. Proof strategies that lose $O(\delta)$ slack against $H$ are
legitimate for the conjecture (its constants are not corner-exact).
\item \textbf{What is already impossible.} A proof cannot proceed by: LP support-cleanup
of optimal exposedness witnesses (pushed-witness death certificate: any negative leakage
breaks dual optimality); the canonical-deficit energy method (anti-lemma: its energy is
$O(\delta\Omega^2)$); naive compactness to $\delta=0$ (the visible set $\W$ jumps in
limits); uniform sup-leakage band closure (the sup is $v$'s own $\delta$-budget of
negative entries --- irreducible, but \emph{benign}: the positive kernel closes exactly
on every measured instance). Five of ten independent proof-strategy kinds collapse into
the exposedness-LP frame at the moment hiddenness is used as a hypothesis (the normal
cone of the hiddenness constraint \emph{is} the LP dual cone); a proof must either live
in that frame or avoid hiddenness via a surrogate (e.g.\ distance to the
Baake--Sumner normal form, the audited canonical W-free restatement).
\item \textbf{What is already real.} Exact rational instances exist with a hidden vertex,
$\sigt_v>0$, and an \emph{entirely shallow} optimal witness face --- but only at height
$H=O(\delta)$ and $\sigt_v<\tau$ (inside the proved branch). Any proof of the conjecture
must tolerate these; any refutation must do strictly better than them.
\item \textbf{Wave-15/16 constraints (2026-06-11).} (a) \emph{No chain-local
certificate exists}: the scalar shadow of the thin-chain inequality is false (exact
rational witnesses for every chain length $L=2,\dots,5$), so any proof must consume the
hiddenness/realization constraints --- aggregate sums alone cannot close it.
(b) \emph{Clone invariance is mandatory}: every intermediate quantity in a proof must be
invariant under duplicate-index splitting (raw atom-level path products are not;
masses, distances, functionals, and quotient weights are). (c) \emph{The $\sigt$ gate alone is crossable}: an exact rational instance ($n=7$,
$k=4$) has a hidden top vertex with $\sigt_v/\tau=1.626$ --- independently certified
(exact idempotence, all decision margins $\ge10^{-3}$ against $5\times10^{-7}$
rationalization drift), with the family persisting to $\delta\le0.1$
($\sigt/\tau=1.03$ at $\delta=0.091$). A height-free barrier
``hidden $\Rightarrow\sigt_v\le C_0\sqrt\delta$'' is therefore \emph{false}. But the
instance has $H/\tau=0.0158$: the joint antecedent of both floor conjectures
($\sigt_v>\tau$ \emph{and} $H>B\tau$) has still never been entered --- the open
question is now the quantitative $\sigt$--$H$ \emph{tradeoff} for hidden vertices. (d) \emph{The anti-splitting frontier}: the proved, clone-invariant
carrier-mass bound $A_v(S_t\setminus C_{\W})\ge(B/3-4)\tau$ stands one dimension-free
pinning step away from the finisher; a named decider target for both directions is the
\emph{shallow fan} (a hidden $v$ spreading $O(\tau)$ positive mass over many
non-coincident quotient classes under a far top-band averaged blocker).
\item \textbf{The variety programme (waves 18--20, 2026-06-11).} Exploiting the exact
quadratic constraint directly: $\{P^2=P,\ P\mathbf1=\mathbf1,\ \mathrm{rank}\,P=k\}$ is
a homogeneous space of dimension $(n-k)(2k-1)$ with pure-corner tangent spaces
($P_0A+AP_0=A$, $A\mathbf1=0$) and an exact chart whose diagonal deviations are
quadratic. \emph{Proved and independently audited:} the \textbf{tangent-cone lemma} ---
at every H--M normal-form point $P_0$ and every variety tangent $A$, along any exact
$C^1$ arc,
\[
\dot H^+_{P_0}(A)\ \le\ 2\,\dot\delta_{P_0}(A),\qquad
\dot\delta_{P_0}(A)=\max_i\sum_{j:P_{0,ij}=0}(-A_{ij})_+,
\]
with the constant $2$ independent of $n$, $k$, the partition, and the block masses
(sharp for the frozen recurrent-hull derivative) --- the infinitesimal form of the
linear law, hiddenness-free and clone-invariant. \emph{Also proved and audited (with repairs):} the \emph{ambient fixed-mass visibility
lemma} (recurrent vertices with LP support margin $\eta$ stay visible for
$\varepsilon\le\min\{\mu/8,\tau/64,\eta\tau/64,1/64\}$ --- ambient, disarming the
recorded W-jump compactness obstruction at fixed mass), and the \emph{mass-removed
boundary-recoding lemma}: an exact H--M recode to a boundary stratum with
$\|P_0-P_0'\|_{\infty,1}\le2(\sum_s q_s+\max_i r_i)$, all bounds in \emph{original}
removed mass --- valid only in the one-shot final-profile form (stepwise iteration
provably overcharges by $O(n)$). The fixed-base second-order race on the dangerous
cone $\dot\delta=0$ is empirically \emph{empty} (clean-window ratio $0$); all
sharpness comes from boundary-crossing arcs, which the recoding now handles.
\emph{The remaining gap to the local linear law is one named estimate}: the
finite-jet normal projection bound $\|(C,D)_{\perp\mathcal M}\|^2\le L\,\delta$ in
the exact chart after final-profile rebasing (equivalently: second-order rigidity of
the $\delta=0$ locus). Local numerics: the worst stable ratio is
$H/\delta=2.000000000013$ --- the local law appears to hold with exactly the lemma's
constant.
\item \textbf{The $\delta=0$ anchor.} At $\delta=0$ both conjectures hold by the
finite stochastic-idempotent normal form of H\"ogn\"as--Mukherjea,
\emph{Probability Measures on Semigroups}, Thm.~1.16; local extraction
\texttt{refs/hognas-mukherjea-2011/hognas-mukherjea-2011.txt:2767--2777}
(extraction-level provenance: byte-checked against the \texttt{pdftotext}
output, not against PDF bytes). In H--M notation a stochastic idempotent
has a basis $\{T_c,C_1,\ldots,C_k\}$; each $C_s\times C_s$ block has one
positive probability row, off-diagonal recurrent blocks vanish, and the
ratio identity for $i\in T_c$ gives $P_{i,C_s}=\alpha_{is}\pi_s$. Since
columns in $T_c$ are zero and rows sum to one, $\alpha_{is}\ge0$ and
$\sum_s\alpha_{is}=1$. Hence the geometrically distinct row vertices are
exactly the recurrent equal-input block rows $\pi_s$, and every transient
row lies in their convex hull. The proof source is H--M Theorem~1.11
(statement \texttt{:2225--2244}; proof via Theorem~1.18,
\texttt{:3079--3210}), not merely the Baake--Sumner reformulation.
\end{enumerate}

\end{document}
