\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{booktabs,longtable,array}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{microtype}

\hypersetup{
  colorlinks=true,
  linkcolor=blue!60!black,
  urlcolor=blue!60!black,
  citecolor=blue!60!black
}

\newcommand{\R}{\mathbb{R}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\conv}{\operatorname{conv}}
\newcommand{\dist}{\operatorname{dist}}
\newcommand{\negm}{\operatorname{neg}}
\newcommand{\diam}{\operatorname{diam}}
\newcommand{\status}[1]{\textsf{#1}}
\newcommand{\todoopen}{\status{open}}
\newcommand{\ready}{\status{ready}}
\newcommand{\conditional}{\status{conditional}}
\newcommand{\false}{\status{false}}
\newcommand{\evidence}{\status{evidence}}
\newcommand{\canonical}{\status{canonical}}
\newcommand{\af}{\status{af}}
\newcommand{\pathref}[1]{\path{#1}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{conjecture}{Conjecture}
\newtheorem{result}{Result}
\newtheorem{warning}{Warning}
\newtheorem{openproblem}{Open Problem}

\title{Agent B Classical Path Report\\
\large Work on \texttt{op-exposed-hull}, 2026-06-07}
\author{Agent B exploration lane}
\date{Checkpoint after commit \texttt{fa2c032}}

\begin{document}
\maketitle

\begin{abstract}
This document reports the Agent B exploration work on the classical
\texttt{op-exposed-hull} route performed on 2026-06-07.  It is a sandbox
report, not a canonical project paper section and not an upgrade of any
registry status.  The report records the target, all definitions introduced
or used by the session, the conjectural proof architecture, the results that
were proved at exploration level, the false shortcuts found, the numerical
and literature evidence, and the current assessment of promise.

The main conclusion is that the classical route remains promising but is not
closed.  The work reduces the route to a sharply localized closed-bad-class
augmentation problem.  Most local finite-dimensional pieces are
proof-ready.  The current blocker cut is
\[
\begin{aligned}
  C9  &\quad\text{(q/shadow interface)},\\
  C12 &\quad\text{(alpha budget or calibrated dual)},\\
  C13 &\quad\text{(separated-circuit negative-mass lower bound)}.
\end{aligned}
\]
The latest C9 campaign killed two tempting shortcuts: distributional
q-quasi-closure does not imply rowwise closure, and Step 3 height control
does not give \(O(\tau)\) leakage for arbitrary shadow witnesses.  The
surviving C9 target is a coupled averaging law \(\pi=m\) controlling both
q-flow and the shadow kernel, or else a route to the C12 calibrated-dual
obstruction.
\end{abstract}

\tableofcontents

\section{Status Vocabulary And Scope}

The following status labels are used throughout this report.
\begin{description}[leftmargin=2.8cm,style=nextline]
\item[\canonical{}] A statement already in the canonical registry/report.
This report does not change such status.
\item[\af{} validated] A canonical statement with an adversarial proof
workspace validated by the existing project machinery.  No new such result
was produced in this session.
\item[\ready{}] An Agent B exploration statement with a complete local proof
outline, small enough to be proposed to Agent A for canonical packaging.  It
still needs formulation review, byte-grounding of any external facts, and
the Recipe A/B/af pipeline before becoming canonical.
\item[\conditional{}] A statement proved modulo a named extra hypothesis.
\item[\todoopen{}] A plausible target with no complete proof.
\item[\false{}] A tempting statement refuted by an explicit argument or
finite counterexample.
\item[\evidence{}] Numerical or literature evidence only.
\end{description}

All work reported here stayed in the Agent B lane:
\pathref{agent-B/**}, \pathref{docs/plans/**}, and
\pathref{docs/worklog.md}.
Canonical layers \pathref{definitions/}, \pathref{argument/},
\pathref{proofs/}, and \pathref{report/} were not used to promote
any new theorem.  The underlying canonical open problem remains
\texttt{op-exposed-hull}.

\section{Canonical Starting Point}

The project already has a classical reduction in the registry.  The relevant
open target is the global exposed-hull lemma for exact signed affine
retractions.  The canonical definition index contains the definitions
\texttt{def-stochastic}, \texttt{def-exposed}, and
\texttt{def-near-positive-projection}; this report uses them by reference
rather than redefining the canonical shards.

\begin{conjecture}[Global exposed-hull target, registry \texttt{op-exposed-hull}]
\label{conj:op-exposed-hull}
There are universal constants \(c,C,C'>0\) such that for every exact signed
affine retraction \(P\), with rows \(p_i\), satisfying
\[
  P\one=\one,\qquad P^2=P,\qquad \negm(p_i)\leq \delta,
\]
and with \(\tau=\sqrt{\delta}\), \(\rho=C\tau\), \(\kappa=c\tau\), every row
satisfies
\[
  \dist_1(p_i,\conv W_{\rho,\kappa})\leq C'\tau.
\]
Here \(W_{\rho,\kappa}\) is the set of row vertices of
\(K=\conv\{p_i\}\) whose exposedness modulus at scale \(\rho\) is at least
\(\kappa\).
\end{conjecture}

If Conjecture~\ref{conj:op-exposed-hull} is proved, the existing
cluster-representative classical theorem gives a stochastic idempotent within
the sharp \(O(\sqrt{\delta})\) scale.  Hume's family shows that the square-root
scale is the right scale; the session found no evidence that Hume obstructs
the exposed-hull formulation.

\section{Definitions Used Or Introduced In The Session}

The definitions in this section are session-level working definitions.  They
are included so that later proof packages have a precise vocabulary.  They
are not canonical definition shards.

\begin{definition}[Signed affine retraction]
A matrix \(P\) is a signed affine retraction if its rows \(p_i\in\R^n\) have
row sum \(1\) and
\[
  P\one=\one,\qquad P^2=P.
\]
Equivalently, each row is fixed by right multiplication:
\[
  p_iP=p_i=\sum_j p_i(j)p_j.
\]
\end{definition}

\begin{definition}[Negative mass]
For a signed probability vector \(x\), set
\[
  \negm(x)=\sum_{j:x_j<0}(-x_j).
\]
Then \(\|x\|_1=1+2\negm(x)\).  The standing small-defect hypothesis in the
classical path is \(\negm(p_i)\leq\delta\) for all rows.
\end{definition}

\begin{definition}[Sharp parameter]
Throughout the session
\[
  \tau=\sqrt{\delta}.
\]
The exposedness and separation scales are
\[
  \rho=R\tau,\qquad \kappa=k\tau
\]
with universal constants chosen in a hierarchy.
\end{definition}

\begin{definition}[Exposedness modulus]
For a row vertex \(v=p_a\) and scale \(\rho\), let
\[
  S_v(\rho)=\{i:\|p_i-v\|_1\geq\rho\}.
\]
The exposedness modulus is
\[
  e_v(\rho)=\sup_h\min_{i\in S_v(\rho)}h(p_i),
\]
where \(h\) ranges over affine functions on \(\operatorname{aff}K\) with
\[
  h(v)=0,\qquad 0\leq h(p_i)\leq 1\quad\text{for all rows }i.
\]
The well-exposed row-vertex set is
\[
  W_{\rho,\kappa}=\{v:\ v\text{ is a row vertex and }e_v(\rho)\geq\kappa\}.
\]
\end{definition}

\begin{definition}[Skeleton and bad rows]
A skeleton \(R_0\) is a maximal \(4\rho\)-separated subset of
\(W_{\rho,\kappa}\), and \(C=\conv R_0\).  A bad row, relative to a threshold
\(D\tau\), is a row satisfying
\[
  \dist_1(p_i,C)>D\tau.
\]
In the closed-bad-class block the bad set is enlarged by \(\rho\)-clusters
when vertex language is required.
\end{definition}

\begin{definition}[Positive-coordinate repair]
For each row let \(a_i=\negm(p_i)\), write \(p_i=p_i^+-p_i^-\), and define
\[
  q_i=\frac{p_i^+}{1+a_i}.
\]
Then \(q_i\) is a probability vector.  The matrix \(q=(q_i)\) is the repaired
positive-coordinate Markov kernel.  For a bad set \(B\), write
\[
  T=q|_{B,B},\qquad s_i=q_i(B^c)=1-\sum_{j\in B}T_{ij}.
\]
\end{definition}

\begin{definition}[Bad lifetime and fundamental matrix]
For a substochastic block \(T=q|_{B,B}\), the killed-chain fundamental matrix
is
\[
  N=(I-T)^{-1}=\sum_{m\geq0}T^m
\]
when \(\rho(T)<1\).  The quantity
\[
  \|N\|_{\infty\to\infty}
\]
is the maximal expected number of visits to \(B\) before exit.
\end{definition}

\begin{definition}[Separator height and high slices]
Let \(\phi\) be an affine separator with \(l_\infty\)-dual norm at most \(1\).
Set
\[
  M=\max_j\phi(p_j),\qquad h_i=M-\phi(p_i).
\]
The high slice of width \(\gamma\) is
\[
  H_\gamma=\{i:h_i\leq\gamma\}.
\]
The two slices used in C9 are
\[
  H_0=B\cap\{h_i\leq A_0\delta\},\qquad
  H_1=B\cap\{h_i\leq G\tau\}.
\]
\end{definition}

\begin{definition}[Shadow witness and shadow kernel]
If a vertex \(u\) fails \(e_u(\rho)\geq\kappa\), a shadow witness is a
probability measure \(\sigma_u\) supported on rows at distance at least
\(\rho\) from \(u\) and with controlled separator-height loss.  A shadow
kernel \(S\) on a high bad set \(H\) is a substochastic matrix whose row
\(S_i\) is such a witness, restricted to \(H\).  Its row loss is
\[
  1-S\one.
\]
\end{definition}

\begin{definition}[Failed-exposedness circuit data]
For a non-exposed vertex \(v\), Step 5 produces data
\[
  \mu\in\Delta(S_v(\rho)),\qquad \alpha_i,\beta_i\geq0,
\]
with
\[
  \sum_{j\in S_v(\rho)}\mu_j(p_j-v)
  =
  \sum_i(\beta_i-\alpha_i)(p_i-v),\qquad
  \sum_i\beta_i<\kappa.
\]
The \(\beta\)-side is controlled.  The \(\alpha\)-side lies on the zero face
of an optimal exposing functional and is the major aggregation obstruction.
\end{definition}

\begin{definition}[Aggregation parameters]
The blocker interaction uses
\[
\begin{aligned}
  \xi    &= \text{q-closure/stationarity error},\\
  M      &= \text{averaged alpha mass},\\
  \theta &= \text{separated witness mass},\\
  E      &= \text{aggregation residual}.
\end{aligned}
\]
The intended closing scale is
\[
  \xi=O(\tau),\qquad M\leq C/\tau,\qquad
  \theta\geq c\tau,\qquad E=O(\delta).
\]
\end{definition}

\begin{definition}[Pi-coupled q/shadow closure]
The corrected C9 interface asks for a probability law \(\pi\) on a high bad
set \(H\) such that
\[
  \pi q(H^c)\leq \xi_q,\qquad
  \|\pi S-\pi\|_1\leq \xi_S,\qquad
  \pi(1-S\one)\leq \xi_S.
\]
The most promising case is \(\pi=m\), the occupation or quasi-stationary law
produced by the bad-kernel lifetime alternative.
\end{definition}

\section{Proof Architecture Developed In The Session}

The best current architecture is not pure convex geometry.  It is
\[
\begin{gathered}
\text{maximal exposed skeleton}\\
\longrightarrow\ \text{positive-coordinate Markov kernel from }P^2=P\\
\longrightarrow\ \text{bad-kernel resolvent alternative}\\
\longrightarrow\ \text{long-lived closed-bad-class alternative}\\
\longrightarrow\ \text{LP/circuit augmentation contradiction}\\
\longrightarrow\ \text{\texttt{op-exposed-hull}.}
\end{gathered}
\]
The crucial reason to use the repaired kernel is that every q-step costs only
order \(\delta\).  Therefore an expected bad lifetime of order \(1/\tau\)
accumulates only order \(\delta/\tau=O(\tau)\), which is exactly the target
scale.

\subsection{Primary Route: Maximal Skeleton And Bad Kernel}

Choose \(R_0\) maximal \(4\rho\)-separated in \(W_{\rho,\kappa}\).  If every
row is \(O(\tau)\)-close to \(C=\conv R_0\), the classical cluster theorem
finishes.  Otherwise form a bad set \(B\).  The proof splits:
\begin{enumerate}[label=\arabic*.]
\item If the bad-to-bad q-block \(T\) has
\[
  \|(I-T)^{-1}\|_{\infty\to\infty}\leq C/\tau,
\]
then all bad rows reconstruct from \(C\) at \(O(\tau)\) cost.
\item If not, finite Markov algebra produces a long-lived q-quasi-closed bad
distribution.  The remaining task is to prove that such a high bad class
contains a new well-exposed vertex far from \(R_0\), contradicting maximality.
\end{enumerate}

\subsection{Secondary Route: Robust Coordinates}

The robust-coordinate route constructs affine coordinates on selected
representatives with row reconstruction \(O(\tau)\) and coordinate negative
mass \(O(\delta)\).  Pushing canonical row coordinates through a stochastic
kernel preserves \(O(\delta)\) negative mass, but the representative
interpolation matrix \(G\) must satisfy
\[
  \max_b\sum_a|G_{ba}-\delta_{ba}|=O(\delta).
\]
A merely \(O(\tau)\) interpolation error exactifies through \(G^{-1}\) and can
create \(O(\tau)\) coordinate negativity, losing the target rate.  Numerical
LP probes nevertheless found \(O(\delta)\) interpolation defect in the tested
Hume, quadrilateral, and small-defect exact similarity examples.  This route
is promising but secondary.

\section{Results Proved Or Isolated}

No new canonical theorem was proved.  The results below are exploration-level
proof packages or refutations.  Each must still go through Agent A review and
the local provenance rules before becoming a registry result.

\subsection{Ready Local Lemmas}

\begin{longtable}{p{0.20\linewidth}p{0.13\linewidth}p{0.57\linewidth}}
\toprule
Label & Status & Statement and proof content\\
\midrule
\endhead
C0 positive-coordinate repair &
\ready{} &
For \(q_i=p_i^+/(1+\negm(p_i))\),
\[
  \left\|p_i-\sum_jq_i(j)p_j\right\|_1\leq 4\delta.
\]
This follows directly from \(p_iP=p_i\), the sign split
\(p_i=(1+a_i)q_i-a_ir_i\), and \(\|p_j\|_1\leq1+2\delta\).\\
\addlinespace
C1 bad-kernel resolvent &
\ready{} &
If \(G=B^c\) rows are \(\Gamma\)-close to a convex set \(C\), and
\(L=\|(I-T)^{-1}\|_{\infty\to\infty}\), then every bad row satisfies
\[
  \dist_1(p_i,C)\leq\Gamma+4\delta L.
\]
The proof uses convexity of distance and
\((I-T)^{-1}(1-T\one)=\one\).\\
\addlinespace
C2 lifetime to occupation measure &
\ready{} after review &
For a finite substochastic \(T\), either
\[
  \|(I-T)^{-1}\one\|_\infty\leq L
\]
or there is a probability \(\mu\) with
\[
  \mu(1-T\one)\leq 1/L,\qquad \|\mu T-\mu\|_1\leq 2/L.
\]
The proof is the normalized occupation measure of a long-lived starting row.\\
\addlinespace
C3 distance separator &
\ready{} with source caveat &
If \(p_i\) is \(H\tau\)-far from a convex hull \(C\), finite
\(\ell_1/\ell_\infty\) separation gives affine \(\phi\) with
\(\|\phi\|_*\leq1\) and
\[
  \phi(p_i)\geq \sup_C\phi+H\tau.
\]
Canonical use needs either an internal finite proof or a byte-verified source.\\
\addlinespace
C4 high-slice drift &
\ready{} &
If \(\|p_i-\sum_jq_i(j)p_j\|_1\leq\varepsilon\), \(\phi\) is
\(L_\phi\)-Lipschitz, \(h_i=M-\phi(p_i)\), and
\(H_\gamma=\{h\leq\gamma\}\), then
\[
  q_i(H_\gamma^c)\leq \frac{h_i+L_\phi\varepsilon}{\gamma}.
\]
This is a one-line Markov inequality applied to
\(\sum_jq_i(j)h_j\leq h_i+L_\phi\varepsilon\).\\
\addlinespace
C5 high-slice bad closure &
\conditional{} &
With bad-set exit \(s_i=q_i(B^c)\),
\[
  q_i((B\cap H_\gamma)^c)
  \leq s_i+\frac{h_i+L_\phi\varepsilon}{\gamma}.
\]
Rows in an \(O(\delta)\) top core map into a \(G\tau\) high slice with
\(O(\tau)\) leakage, provided their bad-set exit is \(O(\tau)\).\\
\addlinespace
C6 top-face exposure &
\ready{} &
If \(u\) maximizes \(\phi\), and every row outside \(B_1(u,\rho)\) has
\(\phi(u)-\phi(p_i)\geq\Delta_\phi\), then
\[
  e_u(\rho)\geq \Delta_\phi/M_\phi,\qquad
  M_\phi=\max_i(\phi(u)-\phi(p_i)).
\]
For \(\|\phi\|_*\leq1\), \(M_\phi\leq 2+4\delta\).\\
\addlinespace
C7 shadow edge &
\ready{} with global-max hypothesis &
If \(u\) is a global \(\phi\)-maximizer and \(e_u(\rho)<\kappa\), then there
is a row \(j\) with \(\|p_j-u\|_1\geq\rho\) and
\[
  \phi(p_j)\geq \phi(u)-(2+4\delta)\kappa.
\]
If \(u\) is \(H\tau\)-above \(C\), then \(j\) remains
\((H-(2+4\delta)k)\tau\)-above \(C\).\\
\addlinespace
C8 shadow recurrence &
\conditional{} &
For a substochastic shadow kernel \(S\) on finite \(H\) with row sums at
least \(1-\varepsilon_s\), the row-normalized chain has a recurrent class and
a probability \(\pi\) with
\[
  \|\pi S-\pi\|_1\leq\varepsilon_s.
\]
If \(H\) is rowwise q-closed, then also \(\pi q(H^c)\leq\varepsilon_q\).\\
\addlinespace
C10 failed-exposedness circuit &
\ready{} &
If \(e_v(\rho)<\kappa\), finite minimax and LP duality give
\[
  \sum_{j\in S_v(\rho)}\mu_j(p_j-v)
  =
  \sum_i(\beta_i-\alpha_i)(p_i-v),
  \qquad \sum_i\beta_i<\kappa,
\]
with complementarity support: \(\alpha\) on the zero face and \(\beta\) on
the top face.  The \(\alpha\)-mass is uncontrolled.\\
\bottomrule
\end{longtable}

\subsection{Small-Case And Model Results}

\begin{longtable}{p{0.22\linewidth}p{0.14\linewidth}p{0.54\linewidth}}
\toprule
Label & Status & Content\\
\midrule
\endhead
Rank \(\leq2\), \(n=3\), simplex row polytopes &
\ready{} / exact &
Segment and simplex barycentric coordinates show all vertices are
\(\kappa\)-exposed at the required square-root scale for suitable constants,
and every row lies exactly in their hull.\\
\addlinespace
Explicit \(n=4\) quadrilateral family &
\ready{} / exact &
For the family \(P_t=I-uv^T\) with \(\delta=t^2\), all four row vertices are
well exposed at \(\rho=t\).  Gurobi verified the exposedness LP at
\(t=1/10\) with objective \(0.99\).\\
\addlinespace
General \(n=4\), rank \(3\), \(2|2\) circuit &
\ready{} at coefficient level &
For a positive circuit
\[
  a p_0+b p_1=c p_2+d p_3,\qquad a+b=c+d=1,
\]
the value assignments expose \(p_0,p_1,p_2,p_3\) at levels \(b,a,d,c\).
If one coefficient is \(<k\tau\), the controlled vertex is within
\(O(k\tau)\) of the opposite edge.\\
\addlinespace
Robust-coordinate push-forward &
\ready{} conditional &
If a stochastic kernel \(U\) reconstructs rows from representatives, then
canonical coordinates pushed through \(U\) satisfy
\[
  \negm(\lambda(p_i))\leq\negm(p_i)\leq\delta.
\]
The remaining need is \(G=I+O(\delta)\) in row-\(\ell_1\) operator norm.\\
\addlinespace
Exact representative reconstruction implies \(G=I\) &
\ready{} &
If \(p_j=\sum_aU_{ja}r^a\) exactly and the representatives are affinely
independent, then applying \(r^b=r^bP\) forces
\[
  G_{ba}=\sum_jr^b_jU_{ja}=\delta_{ba}.
\]\\
\bottomrule
\end{longtable}

\subsection{C9 Campaign Results}

\begin{longtable}{p{0.18\linewidth}p{0.14\linewidth}p{0.58\linewidth}}
\toprule
Label & Status & Content\\
\midrule
\endhead
C9-A high-core pruning &
\ready{} with hypothesis &
For \(H_0=B\cap\{h\leq A_0\delta\}\), \(H_1=B\cap\{h\leq G\tau\}\), and a
probability \(m\) on \(B\),
\[
  \begin{aligned}
    \nu q(H_1^c)&\leq \eta/m(H_0)+((A_0+4)/G)\tau,\\
    \nu&=m|_{H_0}/m(H_0).
  \end{aligned}
\]
Thus sufficient high-core mass gives distributional q-closure into \(H_1\)
and rowwise pruning on most of \(\nu\).\\
\addlinespace
C9-A fallback refutation &
\false{} &
The statement ``small \(m(H_0)\) implies a Lyapunov/resolvent fallback'' is
false for an arbitrary quasi-stationary bad measure.  A stochastic idempotent
with two closed states, one at height \(0\) and one at height \(G\tau/2\), can
have \(m(H_0)=0\), zero exit, and no drift.  The missing datum is return mass
to the high core.\\
\addlinespace
C9-B Step 3 leakage &
\ready{} and limiting &
Step 3 gives only
\[
  \mu(H_1^c)\leq (2+4\delta)k/G,
\]
not \(O(\tau)\), for arbitrary failed-exposedness witnesses.  Therefore
high-supported shadow witnesses require extra q-compatibility or an LP
minimum-leakage condition.\\
\addlinespace
C9-B q-leakage &
\ready{} &
For the repaired kernel,
\[
  q_i(H_1^c)\leq (c_0+4)\tau/G
\]
when \(h_i\leq c_0\delta\).  This is the correct q-side leakage estimate, but
arbitrary shadow witnesses need not be q-side witnesses.\\
\addlinespace
C9-C Lyapunov package &
\ready{} &
For a killed finite kernel, a bounded potential with drift \(c\tau\) gives
\[
  \|(I-T)^{-1}\|_{\infty\to\infty}=O(1/\tau).
\]
Failure of this resolvent bound yields a quasi-stationary occupation measure
with \(O(\tau)\) exit and \(O(\tau)\) stationarity defect.\\
\addlinespace
C9-D distributional-to-rowwise refutation &
\false{} &
The deterministic path
\[
  q_i=\delta_{i+1}\ (i<N),\qquad q_N(B^c)=1,\qquad m_i=1/N
\]
has \(mq(B^c)=1/N\) and \(\|mT-m\|_1=2/N\), but every nonempty subset has a
row with full leakage.  Thus distributional q-quasi-closure alone cannot
produce a rowwise closed core.\\
\addlinespace
C9-D pi-coupled replacement &
\conditional{} / \todoopen{} interface &
The useful replacement is a common averaging law \(\pi\) satisfying
\[
  \pi q(H^c)=O(\tau),\quad \|\pi S-\pi\|_1=O(\tau),\quad
  \pi(1-S\one)=O(\tau).
\]
The preferred route is \(\pi=m\), the bad-kernel occupation law.  Proving
shadow witnesses approximately stationary for the same \(m\) is open.\\
\addlinespace
C9-E repaired scoring &
\evidence{} &
In \(4473\) scored direct \(P=AB\), \(BA=I\) reports, no C9 failure was
found.  Top threats had nonempty bad sets but \(bad\_lifetime=1\), zero
shadow-leakage proxy, and q-exit in the benign one-step regime.\\
\addlinespace
C9-F frozen LP diagnostic &
\evidence{} &
The frozen-row model found no small-\(\delta\) C9 failure.  Hume and direct
small-defect examples stop by exposed augmentation or no bad class.  A regular
12-gon realizes the frozen failure pattern only at large negative mass
\(\delta\approx0.205\).\\
\bottomrule
\end{longtable}

\section{False Shortcuts And Necessary Caveats}

The session improved the proof state partly by finding statements that must
not be used.

\begin{warning}[Pure convex geometry is insufficient]
Dense polygon and cyclic-chain examples show that sequential pointwise
deletion or local exposed-or-redundant reasoning can cycle.  The proof must
use \(P^2=P\) and \(\negm(p_i)\leq\delta\).
\end{warning}

\begin{warning}[One-scale high-slice closure is too strong]
The drift bound gives
\[
  q_i(H_{G\tau}^c)\leq (h_i+4\delta)/(G\tau).
\]
Rows with \(h_i=O(\tau)\) therefore give only constant leakage.  The correct
rowwise statement is two-scale:
\[
  O(\delta)\text{ top core}\longrightarrow G\tau\text{ high slice with }
  O(\tau)\text{ leakage}.
\]
\end{warning}

\begin{warning}[Small high-core mass does not force drift]
As recorded in C9-A, an arbitrary quasi-stationary measure may live forever
on a lower closed class.  A fallback needs return information or a genuine
Lyapunov potential, not only \(m(H_0)\) being small.
\end{warning}

\begin{warning}[Distributional q-closure is not rowwise closure]
The deterministic path example of C9-D shows that
\[
  mq(B^c),\ \|mT-m\|_1=O(\tau)
\]
does not imply any nonempty subset with rowwise \(O(\tau)\) exit.
\end{warning}

\begin{warning}[Shadow leakage is not q-drift]
Step 3/Step 5 witnesses are LP witnesses for failed exposedness.  Unless they
are coupled to \(q_i\), their leakage below a high slice does not imply q-exit
or a q-Lyapunov drift.
\end{warning}

\begin{warning}[Raw affine-circuit lower bound is false]
The stochastic idempotent with rows
\[
  (1,0,0),\quad (0,1,0),\quad (1/2,1/2,0)
\]
has a separated affine circuit and zero negative mass.  Step 7 must restrict
to reduced row-vertex or Step-5 anchored circuits with explicit witness mass
and residual.
\end{warning}

\section{Open Conjectural Interfaces}

\begin{openproblem}[C9: q/shadow interface]
Prove either a pi-coupled interface
\[
  \pi q(H^c)\leq C\tau,\qquad
  \|\pi S-\pi\|_1\leq C\tau,\qquad
  \pi(1-S\one)\leq C\tau
\]
with \(\pi=m\) from the bad-kernel occupation law, or prove that failure of
such q-compatible witness selection produces the C12 alpha-budget or
calibrated-dual obstruction.
\end{openproblem}

\begin{openproblem}[C12: alpha budget or calibrated dual]
In a q-quasi-closed high bad class, choose failed-exposedness witnesses either
with averaged alpha mass \(M=O(1)\), or with a q-compatible calibration whose
residual is \(O(\tau)\) and whose separated witness mass \(\theta\) is
quantified.  The known Step 5 LP duality only controls the \(\beta\)-mass; it
does not control the lower-face \(\alpha\)-mass.
\end{openproblem}

\begin{openproblem}[C13: separated-circuit negative-mass lower bound]
For the reduced or Step-5 anchored aggregate circuit output by C12, prove
\[
  \max_i\negm(p_i)\geq c\,\theta\rho-C E,
\]
or the stronger mass-free version \(c\rho^2-CE\), with explicit dependence on
separated witness mass \(\theta\) and residual \(E\).  If Step 6 supplies only
\(\theta=\Omega(\tau)\), the weak \(\theta\rho^2\) bound is not enough.
\end{openproblem}

\begin{openproblem}[Closed-bad-class augmentation]
Let \(B\) be a high bad row-vertex class farther than \(D\tau\) from
\(C=\conv R_0\), enlarged by \(\rho\)-clusters, and suppose \(B\) is
q-closed in the sense supplied by the long-lifetime alternative.  Prove that
\(B\) contains a row vertex \(w\) with
\[
  \dist_1(w,C)>4\rho,\qquad e_w(\rho)\geq\kappa.
\]
This is blocked exactly by C9, C12, and C13.
\end{openproblem}

\begin{openproblem}[Robust-coordinate interpolation upgrade]
Given a maximal square-root-exposed skeleton \(R\) and rowwise
\(\conv R\)-reconstruction at \(O(\tau)\), find a stochastic kernel \(U\) such
that
\[
  \left\|p_i-\sum_aU_{ia}r^a\right\|_1\leq C\tau
\]
and the representative interpolation matrix satisfies
\[
  \max_b\sum_a\left|\sum_jr^b_jU_{ja}-\delta_{ba}\right|\leq C\delta.
\]
\end{openproblem}

\section{Numerical And Computational Work}

All numerics are evidence only.  They were used to identify false alarms,
constants, and candidate certificate shapes.

\begin{longtable}{p{0.25\linewidth}p{0.65\linewidth}}
\toprule
Artifact & Finding\\
\midrule
\endhead
\pathref{exposed_hull_metrics.py} and family analyzers &
Compute row negative mass, row vertices, exposedness LPs, \(W_{\rho,\kappa}\),
and distance to \(\conv W\).\\
\addlinespace
Hume and Hume products &
Sharp for the \(\sqrt{\delta}\) exponent but not exposed-hull obstructions.
At tested square-root scales the relevant vertices remain well exposed and
rows lie in their hull.\\
\addlinespace
Similarity-conjugated stochastic idempotents &
No serious small-defect threat found.  Missing well-exposed vertices were
very close to the hull of the remaining well-exposed vertices.\\
\addlinespace
Direct exact \(P=AB\), \(BA=I\), \(P\one=\one\) search &
No counterexample found.  Aggressive constants \(\rho=0.5\tau\),
\(\kappa=0.5\tau\) can drop anchor vertices, but the same samples become
harmless for \(\rho\geq\tau\).  Conservative worst finite ratio was about
\(0.1985\).\\
\addlinespace
Small cases and Gurobi LP &
Rank \(\leq2\), \(n=3\), simplex row polytopes, and an explicit \(n=4\)
quadrilateral are benign.  Gurobi 13.0.2 solved an exposedness LP with the
expected objective \(0.99\).\\
\addlinespace
Stress families &
Dense polygons and cyclic chains explain why sequential deletion fails, but
exact polygon projections have constant negative mass and local small-negative
stencils have order-one idempotency defect.\\
\addlinespace
LP/game frozen diagnostic &
The full negation is bilinear/nonconvex before freezing \(P\).  Frozen LPs
separate Hume augmentation from the large-negative-mass regular-polygon
warning.\\
\addlinespace
C9 repaired scorer &
In direct samples, top C9 threats exit in one step or have high-supported
shadow witnesses.  No small-defect long-lived bad trap was seen.\\
\bottomrule
\end{longtable}

\section{Literature Search}

The literature search found no theorem equivalent to
Conjecture~\ref{conj:op-exposed-hull}.  The useful sources are indirect and
must be acquired into local \pathref{refs/} before canonical use.

Highest-priority leads are:
\begin{itemize}[leftmargin=*]
\item Blackwell on idempotent Markoff chains.
\item Schwarz on semigroups of stochastic matrices.
\item Gonzalez--Hartfiel and Gonzalez--Torres on exact stochastic idempotent
matrix spaces and cores.
\item Hoffman and modern Hoffman-constant literature for LP error bounds.
\item Choquet--Corson--Klee and Straszewicz for exposed-point background.
\item Agaev--Chebotarev, Seneta, and related Markov projector/perturbation
work for comparison language around resolvents.
\end{itemize}

The assessment is negative as a proof source: exact stochastic idempotent
structure helps identify the endpoint after the skeleton theorem, but the
dimension-free signed-retraction \(\sqrt{\delta}\) stability estimate appears
to be new.

\section{Promisingness Assessment}

\subsection{Why The Primary Route Is Promising}

The primary route is promising for four concrete reasons.
\begin{enumerate}[label=\arabic*.]
\item The positive-coordinate repair and bad-kernel resolvent half are
small, deterministic, and proof-ready.
\item All stress tests and exact searches so far fail to produce a
small-\(\delta\) counterexample.  The false alarms are explained by bad
constants, constant negative mass, or loss of exact idempotency.
\item The closed-bad-class problem has been decomposed into a finite list of
small contracts.  The blocker cut is now exactly \(\{C9,C12,C13\}\), not an
amorphous gap.
\item The latest C9 work did not merely fail; it identified the correct
replacement interface: use a common law \(\pi=m\) for q-closure and shadow
aggregation, or turn the incompatibility into C12 data.
\end{enumerate}

\subsection{Why The Route Is Still Risky}

The route is still genuinely open.  The risks are:
\begin{enumerate}[label=\arabic*.]
\item C12 may be hard: failed-exposedness LP duality leaves uncontrolled
zero-face \(\alpha\)-mass, and q-quasi-closedness does not automatically see
that mass.
\item C13 needs a reduced or anchored circuit lower bound.  The raw affine
circuit statement is false, so the exact normalization matters.
\item C9 now depends on a coupled witness-selection theorem.  Step 3 alone
cannot supply the desired leakage.
\item Generic Hoffman/convex-geometry black boxes have conditioning problems;
the proof must exploit \(P^2=P\) and row negative mass directly.
\end{enumerate}

\subsection{Recommended Next Work}

The highest-leverage next tasks are:
\begin{enumerate}[label=\arabic*.]
\item Attack C12 directly by minimizing averaged \(\alpha\)-mass in the
failed-exposedness LPs and extracting the dual obstruction.
\item Build a fixed-combinatorics LP/nonlinear model for the C13 medium bound
\[
  \delta\geq c\,\theta\rho-C E
\]
and search for small rational counterexamples before formalization.
\item Reformulate C9 as a \(\pi=m\) witness-selection problem:
\[
  \|mS-m\|_1=O(\tau),\qquad m(1-S\one)=O(\tau),
\]
using q-compatible or minimum-leakage witnesses.
\item Package C0, C1, C2, C4, C5, C6, C7, C8, and C10 for Agent A review as
isolated candidate contracts.
\item Continue the robust-coordinate route only as a certificate-mining
parallel track; its exact interpolation lemma may reduce to the same
closed-bad-class dichotomy.
\end{enumerate}

\section{Artifact Ledger}

The main session artifacts used for this report are:
\begin{itemize}[leftmargin=*]
\item \pathref{agent-B/notes/op-exposed-hull-mission-control.md}
\item \pathref{agent-B/notes/op-exposed-hull-session-2026-06-07.md}
\item \pathref{docs/plans/2026-06-07-op-exposed-hull-attack-plan.md}
\item \pathref{docs/plans/2026-06-07-op-exposed-hull-hard-block-delegation.md}
\item \pathref{docs/plans/2026-06-07-op-exposed-hull-blocker-subplans.md}
\item \pathref{agent-B/notes/subagent-op-exposed-hull-lp-dual.md}
\item \pathref{agent-B/notes/subagent-op-exposed-hull-skeleton.md}
\item \pathref{agent-B/notes/subagent-op-exposed-hull-bad-kernel.md}
\item \pathref{agent-B/notes/subagent-op-exposed-hull-robust-coordinates.md}
\item \pathref{agent-B/notes/subagent-op-exposed-hull-interpolation-upgrade.md}
\item \pathref{agent-B/notes/subagent-op-exposed-hull-computational.md}
\item \pathref{agent-B/notes/subagent-op-exposed-hull-small-cases.md}
\item \pathref{agent-B/notes/subagent-op-exposed-hull-stress-tests.md}
\item \pathref{agent-B/notes/subagent-op-exposed-hull-direct-search.md}
\item \pathref{agent-B/notes/subagent-op-exposed-hull-lp-game.md}
\item \pathref{agent-B/notes/subagent-op-exposed-hull-n4-circuit.md}
\item \pathref{agent-B/notes/subagent-op-exposed-hull-step1-high-slice.md}
\item \pathref{agent-B/notes/subagent-op-exposed-hull-step2-top-face-exposure.md}
\item \pathref{agent-B/notes/subagent-op-exposed-hull-step3-shadow-edge.md}
\item \pathref{agent-B/notes/subagent-op-exposed-hull-step4-shadow-recurrence.md}
\item \pathref{agent-B/notes/subagent-op-exposed-hull-step5-circuit-extraction.md}
\item \pathref{agent-B/notes/subagent-op-exposed-hull-step6-circuit-aggregation.md}
\item \pathref{agent-B/notes/subagent-op-exposed-hull-step7-circuit-lower-bound.md}
\item \pathref{agent-B/notes/subagent-op-exposed-hull-step8-capstone-packaging.md}
\item \pathref{agent-B/notes/subagent-op-exposed-hull-c9a-high-core-pruning.md}
\item \pathref{agent-B/notes/subagent-op-exposed-hull-c9b-shadow-leakage.md}
\item \pathref{agent-B/notes/subagent-op-exposed-hull-c9c-lyapunov-fallback.md}
\item \pathref{agent-B/notes/subagent-op-exposed-hull-c9d-markov-coupling.md}
\item \pathref{agent-B/notes/subagent-op-exposed-hull-c9e-computational-scoring.md}
\item \pathref{agent-B/notes/subagent-op-exposed-hull-c9f-counterexample-lp.md}
\item \pathref{agent-B/notes/subagent-op-exposed-hull-frameworks.md}
\item \pathref{agent-B/notes/subagent-op-exposed-hull-literature.md}
\item \pathref{agent-B/notes/op-exposed-hull-literature-scout-2026-06-07.md}
\item \pathref{agent-B/experiments/op-exposed-hull/}
\end{itemize}

\section{Bottom Line}

The classical path is promising, but the rigorous proof has not landed.  The
session converted a broad search problem into a precise proof program.  The
primary route should now be judged by C9/C12/C13:
\[
\begin{aligned}
  &\text{pi-coupled q/shadow closure}\\
  &\quad+\ \text{alpha-budget/calibrated aggregation}\\
  &\quad+\ \text{anchored separated-circuit lower bound}.
\end{aligned}
\]
If these three statements are true with the stated scales, the remaining
capstone is short.  If any one fails, the existing LP/game diagnostics are
well positioned to produce a concrete counterexample candidate or a revised
interface.  At this checkpoint, no numerical or small-case evidence points to
a small-defect counterexample; the main difficulty is analytic, not
experimental.

\end{document}
