Kitaev showed that a quantum channel which is almost idempotent --- a unital
completely positive map $\Phi$ on the operators of a finite-dimensional Hilbert
space with $\norm{\Phi^2-\Phi}_{\mathrm{cb}}\le\eta$ --- carries, on its
near-fixed points, the structure of an approximate $C^*$-algebra, and that every
finite-dimensional approximate $C^*$-algebra is close to a genuine one. We study
the same question when $\Phi$ is only assumed \emph{positive}, not completely
positive. We show that the correct invariant is then a \emph{Jordan} algebra
rather than an associative one, for a precise structural reason: a positive
unital map need not satisfy the Schwarz inequality $\Phi(x)^*\Phi(x)\le
\Phi(x^*x)$, but it always satisfies Kadison's inequality $\Phi(x)^2\le\Phi(x^2)$
for self-adjoint $x$, and the latter involves exactly the data of a Jordan
algebra.

Our main complete result is a \emph{bridge theorem}: for any unital positive
$\Phi$ with $\norm{\Phi^2-\Phi}\le\eta$, the near-fixed-point space
$A=\Img P$ of the spectral idempotent $P=\theta(2\Phi-\Id)$, equipped with the
product $a\bullet b=P(a\jp b)$, satisfies the axioms of a Jordan algebra up to
an error $O(\sqrt\eta)$, with constants independent of dimension. The proof uses
no dilation and no complete positivity; the key fact is that the ``square holes''
$P(a^2)-a^2$ are almost-positive null elements, so that quadratic error terms are
$O(\eta)$ while the exact Jordan identity of the ambient algebra cancels the
leading term.

We then carry the programme as far as it currently goes and report honestly on
what is proved, conditional, or open. \emph{(i)} We reduce \emph{exact}
factorization by unital positive maps to a single stability question
--- that a near-positive idempotent is $O(\sqrt\eta)$-close to a genuine positive
one --- proving the factorization conditional on it and showing that no
generic positivity-rounding can replace it. \emph{(ii)} In the commutative case
this becomes a stability problem for almost-idempotent stochastic matrices; we
record the sharp square-root exponent, several proved special cases, and an exact
commutative factorization theorem, leaving one geometric lemma open.
\emph{(iii)} For the abstract structure theorem --- every finite-dimensional
approximate Jordan algebra is close to a genuine one --- we present a
dimension-free splitting of the Jordan cohomology coboundary for exact cocycles
on every finite-dimensional JB-algebra (the exact-adjoint benchmark), isolating
the approximate-cocycle and positivity gaps that remain. \emph{(iv)} We analyse
the exponent ($1/2$ in general; $1$ for completely positive maps, and
conjecturally for decomposable maps, conditional on a dilation-compatibility
hypothesis that we make precise). The report is a consensus document of two
collaborating authors; every statement is tagged as a definition, a cited fact,
a proved result, a conditional result, or an open target.
