\section{Introduction}\label{sec:intro}

\paragraph{The question.}
A physical system sometimes hides a smaller logical system inside it: the
logical observables are encoded in the physical ones, and a recovery operation
returns the system to the encoded subspace. Mathematically, such a recovery is a
quantum channel $T$ that is idempotent, $T^2=T$. Kitaev~\cite{Kitaev2024} studied
the realistic case where the recovery is only \emph{approximately} idempotent,
and asked what algebraic structure the encoded observables carry. He worked with
the dual map $\Phi$ of the channel, a unital completely positive map on the
algebra $B(\HH)$ of operators on a finite-dimensional Hilbert space, and measured
non-idempotence by $\norm{\Phi^2-\Phi}_{\mathrm{cb}}\le\eta$. His answer: the
near-fixed points of $\Phi$ form an \emph{approximate $C^*$-algebra}, and every
finite-dimensional approximate $C^*$-algebra is, with universal (dimension-free)
constants, close to a genuine $C^*$-algebra.

\paragraph{This report.}
We ask the same question for maps that are only \emph{positive}, not completely
positive. This is the natural setting whenever one cares about distinguishability
of states rather than full quantum operations, and it is the setting of
van~Luijk and Wilming~\cite{vanLuijkWilming2026}, who show that for positive
trace-preserving maps the relevant invariant is a \emph{Jordan} algebra. The
present report does the following, in order of completeness:
\begin{enumerate}[leftmargin=*]
  \item It records the consensus \emph{definitions} (positive map, Jordan
    product, JB-algebra, order-unit space, approximate Jordan algebra). Standard
    background definitions are matched against local source copies; project
    definitions such as the $\eps$-JB notion are marked \status{(consensus)} and
    tied to internal proof files in \texttt{PROVENANCE.md}.
  \item It proves the \emph{bridge theorem} (\Cref{sec:bridge}): from a unital
    positive almost-idempotent $\Phi$ one obtains, with no use of dilations or
    complete positivity, a space that satisfies the Jordan-algebra axioms up to
    $O(\sqrt\eta)$. This is the positive-map analogue of the first half of
    Kitaev's construction, and it is complete. A companion result
    (\Cref{sec:faithful}) treats the ambient product under a faithful invariant
    state.
  \item It reduces \emph{exact factorization} by unital positive maps
    (\Cref{sec:factorization}) to one stability question about near-positive
    idempotents, proving the factorization conditional on it; in the
    \emph{commutative} case (\Cref{sec:classical}) this becomes a stability
    problem for almost-idempotent stochastic matrices, for which the sharp
    exponent, several proved special cases, and an exact factorization theorem
    are established.
  \item It develops the \emph{abstract structure theorem}
    (\Cref{sec:programme}) --- the analogue of the second half of Kitaev's
    theorem --- proving a dimension-free splitting of the Jordan cohomology for
    exact cocycles on every finite-dimensional JB-algebra, and isolating the
    remaining gaps.
  \item It analyses the \emph{exponent} $\sqrt\eta$ versus $\eta$
    (\Cref{sec:exponent}) and the role of decomposability, and summarises the
    status throughout (\Cref{sec:discussion}).
\end{enumerate}

\paragraph{Why Jordan, and not associative.}
The reason positivity forces a Jordan, rather than associative, structure can be
stated in one line. Kitaev's verification of the $C^*$-norm axiom rests on the
Schwarz inequality $\Phi(x)^*\Phi(x)\le\Phi(x^*x)$, which holds for $2$-positive
(in particular completely positive) maps. A merely positive unital map need not
satisfy it; what it does satisfy is Kadison's inequality
$\Phi(x)^2\le\Phi(x^2)$ for self-adjoint $x$~\cite{Kadison1952}. The latter
involves only self-adjoint elements and squares --- exactly the data on which a
Jordan algebra is built. Replacing the associative product $xy$ by the symmetric
product $x\jp y=\tfrac12(xy+yx)$ throughout is therefore not a convenience but a
necessity, and the entire theory reorganises around it.

\paragraph{Conventions and status flags.}
All Hilbert spaces are finite-dimensional and complex. We write $B(\HH)$ for the
operators on $\HH$ and $\Bsa$ for the self-adjoint ones. Statements carry a
status: \status{(proved)} for results with a complete proof in this report or
transcribed from a verified source; \status{(cited)} for results imported from
the literature; \status{(consensus)} for definitions and conventions adopted by
agreement between the authors; \status{(conditional)} for implications whose
stated hypothesis is still open; \status{(benchmark)} for exact-cocycle or
restricted-module results that do not yet prove the full target;
\status{(obstruction)} for proved no-go statements about a route;
\status{(source-extracted)} for claims supported by local extraction but still
awaiting primary byte-check; \status{(numerical)} for evidence that is not used
as proof; and
\status{(open)} for targets of the programme not yet established. Constants
denoted $C$ are universal and never depend on $\dim\HH$ unless explicitly
stated.

\paragraph{Reading guide (and how to verify it).}
The fastest way to see what is established and what remains is the status ledger
(\Cref{tab:status}) together with the dependency graph (\Cref{fig:dag}), both at
the end of \Cref{sec:discussion}. One complete, unconditional result anchors the
report --- the bridge theorem (\Cref{thm:bridge}), \Cref{sec:bridge} --- and
everything else is organised around it: an exact-factorization reduction
(\Cref{sec:factorization,sec:classical}), the abstract structure programme
(\Cref{sec:programme}), and the exponent question (\Cref{sec:exponent}). The three
genuinely open problems are isolated in \Cref{sec:discussion}. Two further
checkable layers sit under the prose. First, every statement imported from the
literature carries a citation whose bibliography entry links to the source
(arXiv, journal open access) where one is publicly available. Second, results
marked with a green `\textcolor{afgreen}{$\checkmark$\,af-validated}' badge are
machine-checked: the badge links to a self-contained formal workspace
\texttt{proofs/<id>/} whose root statement is byte-identical to the result's
registry contract and whose every step was proved and independently verified.
Sixteen results --- the bridge and its lemmas, the dilation-compatible theorem,
the conditioned faithful-invariant bound, the classical signed/stochastic
equivalence (\Cref{lem:classical-equiv}), and the direct-sum exact-adjoint
splitting (\Cref{prop:direct-sum}) --- are af-validated; they are the
green nodes of \Cref{fig:dag}.
