\section{Exact factorization by positive maps}\label{sec:factorization}

The bridge of \Cref{sec:bridge} turns an almost-idempotent positive map into an
\emph{approximate} Jordan algebra. The original goal of Kitaev's theorem,
however, is sharper: to \emph{factor} the map, up to a small error, through a
\emph{genuine} algebra by structure-preserving maps. This section records what is
known about the positive-map analogue of that factorization. The endpoint is
classical (Effros--St\o rmer); the obstruction is that the spectral idempotent
$P$ is only approximately positive, and rounding it to a genuinely positive map
cannot be done generically. The viable route is a stability statement for
near-positive idempotents, conditional on which we obtain exact unital-positive
factor maps with the bridge exponent (Theorem~C below).

Throughout, $\Phimap\colon\Bsa\to\Bsa$ is unital positive with
$\norm{\Phimap^2-\Phimap}\le\eta$, $P=\theta(2\Phimap-\Id)$ is the spectral
idempotent of \Cref{sec:spectral}, $A=\Img P$, and $a\bullet b=P(a\jp b)$.

\subsection{The exact template}

The factorization we approximate is the exact theorem of Effros and
St\o rmer: a positive unital projection makes its range a genuine Jordan
algebra, and \emph{is} the pair of factor maps.

% PROV: EffrosStormer1979 ocr-pages/page-05.txt L9-16 (Theorem 1.4) -- a unital positive projection P on a unital JC-algebra makes P(A) a JC-algebra under r*s=P(r o s); ocr-pages/page-06.txt L42-44 (Corollary 1.6) -- fixed points of a normal unital positive map on a JW-algebra have a natural JW structure; ocr-pages/page-02.txt L33-38 records Lemma 1.1 used in the proof.
\begin{theorem}[Effros--St\o rmer]\label{thm:effros-stormer}
\status{(cited)}
Let $A$ be a unital JC-algebra and $E\colon A\to A$ a unital positive
projection ($E^2=E$). Then the range $E(A)$, equipped with the vector-space
operations inherited from $A$ and the product
\[
  r\bullet s=E(r\jp s),
\]
is a JC-algebra. Equivalently, the fixed-point set of any normal unital positive
map of a JW-algebra into itself carries a natural JW-algebra structure.
\end{theorem}

\Cref{thm:effros-stormer} is the Jordan analogue of the Choi--Effros
theorem~\cite{ChoiEffros1977} for completely positive projections, and the exact
($\eta=0$) limit of the bridge (\Cref{rem:bridge-exact}). If the spectral
idempotent $P$ of an almost-idempotent $\Phimap$ were \emph{genuinely} positive,
\Cref{thm:effros-stormer} would apply to $E=P$ directly and produce a genuine
JC-algebra $J=P(\Bsa)$ together with exact factor maps. The difficulty is that
$P=\theta(2\Phimap-\Id)$ is only $O(\eta)$-positive
(\eqref{eq:bridge-deltapos}), and may genuinely fail to be positive.

% PROV: ORIGINAL agent-B compaction-checkpoint "Counterexample Boundary" -- explicit classical R^4 stochastic family where Phi is positive unital almost-idempotent but theta(2Phi-I) has negative entries.
\begin{remark}[$P$ can fail to be positive]\label{rem:P-not-positive}
\status{(proved)}
The approximate positivity in \eqref{eq:bridge-deltapos} cannot be upgraded to
exact positivity: there is an explicit classical (commutative) family of
positive unital almost-idempotent maps $\Phimap$ on $\R^4$ for which
$P=\theta(2\Phimap-\Id)$ has strictly negative entries. Thus the projected
product $a\bullet b=P(a\jp b)$ of the bridge is genuinely needed; one cannot
simply invoke \Cref{thm:effros-stormer} for $P$.
\end{remark}

\subsection{Why generic positivity rounding fails}

One might hope to repair $P$ to a positive map abstractly: given a map that is
$\eps$-positive, find a genuinely positive map within $O(\eps)$. \emph{No such
dimension-free repair exists}, even for the simplest non-commutative Jordan
targets. The obstruction uses spin factors.

% PROV: HancheOlsenStormer1984 (spin factor 2.9.7) -- spin factor cone; the order-unit cone of the spin factor.
\begin{definition}[Spin-factor cone]\label{def:spin-cone}
\status{(cited)}
For the spin factor $J=\R\Id\oplus\R^{m}$ (\Cref{thm:jnw-classification}), an
element $(s,v)$ with $s\in\R$, $v\in\R^{m}$ has square
$(s,v)\jp(s,v)=(s^2+\norm{v}_2^2,\,2sv)$ and spectrum $\{s\pm\norm{v}_2\}$. Hence
the positive cone and the order-unit norm are
\[
  J_+=\{(s,v):s\ge\norm{v}_2\},\qquad
  \norm{(s,v)}=\lvert s\rvert+\norm{v}_2 .
\]
A linear map $T$ into $J$ is \emph{$\eps$-positive} if $T(x)\ge-\eps\norm{x}\Id$
for $0\le x\le\Id$.
\end{definition}

% PROV: ORIGINAL agent-B/notes/subagent-positivity-rounding.md and factorization-positivity-rounding.md -- spin-factor target J=R+R^m, domain l_infty^{2m}, eps-positive unital map at distance >= sqrt(eps) from every positive unital map; Rademacher lower bound.
\begin{proposition}[Failure of dimension-free positivity rounding]
\label{prop:rounding-fails}
\status{(proved; obstruction)}
For every integer $m\ge1$ put $\eps=1/(2m)$ and let $J=\R\Id\oplus\R^{m}$ be the
spin factor. Define a unital map $T\colon\ell^{\infty}_{2m}\to J$ on the
coordinate atoms $\delta_{j,\pm}$ \textup{(}$j=1,\dots,m$\textup{)} by
\[
  T(\delta_{j,+})=(\eps,\ 2\eps\,e_j),\qquad
  T(\delta_{j,-})=(\eps,\ -2\eps\,e_j),
\]
where $e_1,\dots,e_m$ is the standard basis of $\R^{m}$. Then $T$ is unital and
$\eps$-positive, yet
\[
  \norm{T-S}\ \ge\ \sqrt{\eps}
  \qquad\text{for \emph{every} positive unital map } S\colon\ell^{\infty}_{2m}\to J.
\]
The same lower bound holds with domain $B(\C^{2m})_{\mathrm{sa}}$, by composing
with the diagonal conditional expectation.
\end{proposition}

\begin{proof}[Proof idea]
Unitality of $T$ holds because the $2m$ atom-images sum to $(1,0)=\Id$;
$\eps$-positivity follows from $2\norm{v}_2\le\sum_j p_j+1$ for a sub-probability
vector $p$. For the lower bound: a \emph{positive} unital $S$ has atom-images
$S(\delta_i)=(s_i,w_i)\in J_+$ with $s_i\ge\norm{w_i}_2$ and
$\sum_i(s_i,w_i)=(1,0)$, whence $\sum_i\norm{w_i}_2\le\sum_i s_i=1$. The
vector parts of $T$ have $\sum_i\norm{v_i}_2=2$. Averaging over Rademacher signs
$\sigma_i\in\{\pm1\}$,
$\mathbb E_\sigma\bigl\Vert\sum_i\sigma_i(v_i-w_i)\bigr\Vert_2^2
   =\sum_i\norm{v_i-w_i}_2^2\ge\eps$,
so some sign pattern gives $\Vert\sum_i\sigma_i(v_i-w_i)\Vert_2\ge\sqrt\eps$,
which is dominated by $\norm{T-S}$ tested against the corresponding element of
$\ell^{\infty}_{2m}$.
\end{proof}

\Cref{prop:rounding-fails} shows that an approximate \emph{algebra} isomorphism
alone cannot deliver exact positive factor maps with the bridge exponent: a
black-box $O(\eps)$ repair is impossible, and any generic repair must lose at
least a square root. Note the obstruction needs a \emph{free} map (no retraction
constraint): the construction does not respect an idempotent relation
$S\circ\iota=\mathrm{id}$. This is exactly the loophole the next subsection
exploits. In the fully commutative case (both domain and codomain commutative)
the obstruction is absent: normalising the positive parts of signed rows yields a
positive unital map within $2\eps$ (this is the starting point of
\Cref{sec:classical}).

\subsection{Near-positive projection stability}

The escape from \Cref{prop:rounding-fails} is to ask for stability of
\emph{idempotents}, not of arbitrary near-positive maps. An idempotent's
retraction constraint pins it to its own range and rules out the cheap
sign-spreading used in the counterexample.

% PROV: ORIGINAL agent-B/notes/near-positive-projection-stability-program.md and theorem-stack-v0.3 Theorem 3 hypothesis -- the sharp noncommutative near-positive projection stability target.
\begin{openproblem}[Near-positive projection stability]\label{op:npps}
\status{(open; sharp exponent $1/2$)}
There exist universal constants $\delta_0,K>0$ \emph{(independent of dimension)}
such that the following holds for every finite-dimensional $\HH$. If
$R\colon\Bsa\to\Bsa$ is linear with
\[
  R^2=R,\qquad R(\Id)=\Id,\qquad \norm{R}\le1+\delta,\qquad
  R(x)\ge-\delta\,\Id\ \text{ for }0\le x\le\Id,
\]
and $0<\delta\le\delta_0$, then there is a unital positive idempotent
$E\colon\Bsa\to\Bsa$ with
\[
  \norm{E-R}\le K\sqrt{\delta}.
\]
\end{openproblem}

The square-root exponent is the best possible: linear ($O(\delta)$) stability is
already false in the commutative case (\Cref{sec:classical}, Hume's example
\Cref{ex:hume}). \Cref{op:npps} is open in general; its commutative reduction and
the special cases now proved are the subject of \Cref{sec:classical}.

\subsection{Conditional exact factorization (Theorem~C)}

Granting \Cref{op:npps}, the factorization goes through with the bridge exponent
and \emph{genuinely positive} factor maps.

% PROV: BRIDGE+EffrosStormer; agent-B/theory/theorem-C-conditional-factorization.md -- conditional exact UP factorization; Delta=inclusion, Upsilon=E; bounds; real-to-complex Effros-Stormer; cone compatibility.
\begin{theorem}[Conditional exact unital-positive factorization]\label{thm:factorization}
\status{(proved, conditional on \Cref{op:npps})}
Assume \Cref{op:npps}. Then there are universal constants $\eta_0,C>0$ such that
the following holds. Let $\HH$ be finite-dimensional and
$\Phimap\colon\Bsa\to\Bsa$ unital positive with
$\norm{\Phimap^2-\Phimap}\le\eta\le\eta_0$. Then there exist a finite-dimensional
special JB-algebra $J$ (a JC-algebra) and \emph{unital positive} maps
\[
  \Delta\colon J\to\Bsa,\qquad \Upsilon\colon\Bsa\to J,
\]
such that
\[
  \Upsilon\Delta=\mathrm{id}_J,\qquad
  \norm{\Delta\Upsilon-\Phimap}\le C\sqrt{\eta},\qquad
  \Upsilon\bigl(\Delta(x)\jp\Delta(y)\bigr)=x\bullet y\ \ (x,y\in J),
\]
where $\bullet$ is the Jordan product of $J$. Concretely $\Delta$ is the
inclusion of $J$ into $\Bsa$ and $\Upsilon=E$ is a unital positive idempotent
with $J=E(\Bsa)$ and $x\bullet y=E(x\jp y)$.
\end{theorem}

\begin{proof}
Form $P=\theta(2\Phimap-\Id)$. By the spectral estimate of \Cref{sec:spectral}
(see \eqref{eq:bridge-delta}--\eqref{eq:bridge-deltapos}), $P$ is a unital
idempotent with $\norm{P-\Phimap}\le C\eta$, $\norm{P}\le1+C\eta$, and
$P(x)\ge-C\eta\,\Id$ for $0\le x\le\Id$. Thus $P$ satisfies the hypotheses of
\Cref{op:npps} with $\delta=C\eta$ when $\eta>0$. If $\eta=0$, then
$P=\Phimap$ is already a unital positive idempotent and we set $E=P$. Otherwise
apply \Cref{op:npps}: there is a unital positive idempotent $E$ with
$\norm{E-P}\le K\sqrt{C\eta}\le C'\sqrt{\eta}$.

Extend $E$ complex-linearly to $E_\C(a+ib)=E(a)+iE(b)$ on $B(\HH)$; since
positivity is tested on positive self-adjoint inputs, $E_\C$ is a unital
positive projection on the JC-algebra $B(\HH)$. By \Cref{thm:effros-stormer},
$J:=E(\Bsa)$ is a JC-algebra under $x\bullet y=E(x\jp y)$; it is special by
construction as the Effros--St\o rmer JC range inside $B(\HH)$ with projected
product $E(x\jp y)$, so the exceptional Albert algebra cannot occur. This does
not assert closure under the ambient product $\jp$.

Set $\Delta=$ the inclusion $J\hookrightarrow\Bsa$ and $\Upsilon=E$. Both are
unital and positive: $\Delta$ maps the cone $J_+=J\cap B(\HH)_+$ into $B(\HH)_+$, and
$E(B(\HH)_+)\subseteq J_+$ because $E$ is positive and idempotent. Then
$\Upsilon\Delta=E|_J=\mathrm{id}_J$, and
\[
  \norm{\Delta\Upsilon-\Phimap}=\norm{E-\Phimap}
   \le\norm{E-P}+\norm{P-\Phimap}\le C'\sqrt\eta+C\eta\le C\sqrt\eta .
\]
The multiplicativity identity $\Upsilon(\Delta x\jp\Delta y)=E(x\jp y)=x\bullet y$
is the definition of the Effros--St\o rmer product. Finally the JB positive cone
of $(J,\bullet)$ equals the inherited cone $J\cap B(\HH)_+$: if $x=y\bullet y=E(y\jp y)$
then $x\ge0$ ambiently by positivity of $E$; conversely $z\in J\cap B(\HH)_+$ with
$m=\norm{z}$ satisfies $\norm{m\Id-z}\le m$, which by the unital JB
norm criterion makes $z$ a positive element of $(J,\bullet)$. Hence the factor
maps are positive for the intrinsic JB order of $J$.
\end{proof}

\Cref{thm:factorization} isolates the entire remaining difficulty in a single
unproved input, \Cref{op:npps}: \emph{the implication is proved}; only the
stability theorem is open. There is no use of abstract positivity rounding (which
\Cref{prop:rounding-fails} forbids) and no use of the abstract structure theorem
of \Cref{sec:programme}; the route is independent of Layer~1. The price is the
exponent: $\sqrt\eta$ rather than $\eta$, which by Hume's example (\Cref{ex:hume})
is the best this route can give.

The factor maps in \Cref{thm:factorization} are unital positive maps. The
theorem does \emph{not} assert decomposable factor maps in general. Such a
strengthening requires additional reversibility or universal-reversibility
input on the exact JC range, as in the exact theory discussed around
\Cref{sec:exponent}.

% PROV: TS3; agent-B/notes/layer1-output-requirements.md.
\begin{remark}[An alternative route through Layer~1]\label{rem:layer1-route}
\status{(open)}
If instead the abstract structure theorem (\Cref{sec:programme}) were proved
with a \emph{positivity-capable} output --- a genuine JC-subalgebra
$J_0\subseteq\Bsa$ whose points are close to the bridge range $A=\Img P$, and a
canonical positive conditional expectation $E_{J_0}$ close to $P$ --- then
comparing $P$ to $E_{J_0}$ would give exact positive factor maps without
invoking \Cref{op:npps}. This route is not yet formalised; algebraic closeness
alone is insufficient, precisely because of \Cref{prop:rounding-fails}.
\end{remark}
