%% Section 8 — Status and open problems.
%% Cross-refs to existing labels: bridge (sec. 6), epsjb (sec. 5),
%% programme (sec. 7). Citation keys per references.bib.
\section{Status and open problems}\label{sec:discussion}

This section records what is proved, what is cited, and what is open. We
separate the two layers of the programme: the \emph{bridge}
(\Cref{sec:bridge}), which turns an almost-idempotent positive map into an
approximate Jordan algebra, and the \emph{structure theory}
(\Cref{sec:programme}), which would turn an approximate Jordan algebra back into a
genuine one. Throughout, $\Phimap\colon\Bsa\to\Bsa$ is unital and positive
($\ast$-preserving) with $\norm{\Phimap^2-\Phimap}\le\eta$,
$P=\theta(2\Phimap-\Id)$ the spectral idempotent close to $\Phimap$,
$A=\Img P$, and $a\bullet b:=P(a\jp b)$.

\subsection{The exponent: \texorpdfstring{$\sqrt\eta$}{root eta} versus
\texorpdfstring{$\eta$}{eta}}

The bridge of \Cref{sec:bridge} produces an $\eps$-JB-algebra with
$\eps=O(\sqrt\eta)$, and this exponent is unconditional. The Kitaev-strength
exponent $\eps=O(\eta)$ is available in the UCP/cb setting treated by
Kitaev, and in any positive-map setting that supplies a compatible lifted-UCP
dilation model. For arbitrary positive maps, and for decomposable maps without
such compatible data, it remains conjectural. The following remark explains why.

% PROV: Kitaev2024 approximate_algebras.tex L2643-2663 (R_k(X)) and L2671-2673 (WXYZOeta-1) -- single insertion R_k has squared norm O(eta), so norm O(sqrt eta); the associativity defect W is bilinear in two such insertions, giving O(eta). Transfers to CP via the Stinespring dilation; unavailable for general positive maps.
\begin{remark}[Why CP gives $\eta$ and positivity gives only $\sqrt\eta$;
\status{(proved for the bridge at $\sqrt\eta$; $\eta$ open)}]
\label{rem:exponent}
Both regimes are governed by a single ``hole'' quantity: the failure of a
single inserted $\Phimap$ (or $P$) to be invisible. For a unital positive
$\Phimap$ a single insertion is controlled only in the seminorm of the state
$\omega=\rho\circ\Phimap$, where Jordan--Schwarz gives a defect of squared size
$O(\eta)$, hence norm $O(\sqrt\eta)$. This is the source of the unconditional
$\eps=O(\sqrt\eta)$. Kitaev's $O(\eta)$ does \emph{not} arise from a single
insertion: the associativity defect is an intrinsically \emph{bilinear} pairing
of \emph{two} holes living in the Stinespring dilation. In his notation the
one-hole vector $R_k(X)$ satisfies
$R_k(X)^\dagger R_k(X)
 =\Phimap^2(\Phimap(X^\dagger)\Phimap(X))
 -\Phimap(\Phimap^2(X^\dagger)\Phimap^2(X))=O(\eta)\norm{X}^2$,
so $\norm{R_k(X)}=O(\sqrt\eta)\norm{X}$, while the defect equals a product
$W=V_1^\dagger R_1(X^\dagger)^\dagger\,u_{3,0}(\Phimap(Y))\,V_3 R_0(Z)$ of two
such vectors, whence $\norm{W}=O(\sqrt\eta)\cdot O(\sqrt\eta)=O(\eta)$ by
Cauchy--Schwarz. The two-hole pairing requires complete positivity (it lives in
the dilation Hilbert space and uses matrix amplifications
$\mathrm{id}_n\otimes\Phimap$); a general positive map has no such dilation, so
only the single-insertion $O(\sqrt\eta)$ bound survives. For
\emph{decomposable} maps
$\Phimap=\Phimap_0+\Psi_0\circ\tau$ (with $\Phimap_0,\Psi_0$ completely positive
and $\tau$ the transpose, with explicit component control such as
$\Phimap_0(\Id)+\Psi_0(\Id)=\Id$) each summand carries a dilation, and we
\emph{conjecture} the two-hole mechanism is restored if those dilation models
can be made compatible, giving $\eps=O(\eta)$; this is \status{(open)}.

\smallskip\noindent\textbf{Agent B review correction.}
The decomposable statement is not a theorem from an arbitrary CP+coCP
decomposition. A linear $\eta$ bound would still require compatible dilation
bookkeeping or a direct cancellation argument for the two holes.
\end{remark}

\subsection{Exact factorization by positive maps}

The bridge yields an \emph{approximate} Jordan algebra and approximate factor
maps. Producing \emph{exact} unital-positive factor maps requires more: either a
concrete genuine Jordan algebra sitting near $A$ inside $\Bsa$, or a stability
statement promoting the idempotent $P$ to a genuine positive idempotent. The
exact endpoint is classical.

% PROV: EffrosStormer1979 ocr-pages/page-05.txt L9-16 (Theorem 1.4) -- a unital positive projection P on a JC-algebra makes P(A) a JC-algebra under r*s=P(r o s); ocr-pages/page-06.txt L42-44 (Corollary 1.6) -- fixed-point set of a normal unital positive map on a JW-algebra has natural JW structure; ocr-pages/page-02.txt L33-38 records Lemma 1.1 used in the proof.
\begin{theorem}[Effros--St\o rmer; \status{(cited)}]\label{thm:effros-stormer}
Let $A$ be a unital JC-algebra and $P\colon A\to A$ a unital positive
projection. Then $P(A)$, equipped with the given vector-space operations and the
product $r\bullet s=P(r\jp s)$, is a JC-algebra. Equivalently, the fixed-point
set of any normal unital positive map of a JW-algebra into itself carries a
natural JW-algebra structure.
\end{theorem}

\Cref{thm:effros-stormer} is the exact template our bridge approximates: it is
the Jordan analogue of the Choi--Effros theorem \cite{ChoiEffros1977} for
completely positive projections. If the spectral idempotent $P$ were genuinely
positive,
\Cref{thm:effros-stormer} would directly furnish a genuine JC-algebra and exact
factor maps. The obstruction is that $P$ is only $O(\eta)$-positive, and one
cannot in general round it to a positive map without loss.

% PROV: ORIGINAL agent-B/notes/factorization-positivity-rounding.md §§2-4 and agent-B/notes/subagent-positivity-rounding.md -- a generic O(eps) positivity-rounding is FALSE; an eps-positive map on l_infty can be sqrt(eps)-far from every positive unital map, via spin-factor targets J = R + R^m.
\begin{remark}[Positivity rounding fails generically; \status{(open)} stability]
\label{rem:rounding}
A generic dimension-free $O(\eps)$ positivity-rounding lemma is \textbf{false}.
There is an $\eps$-positive unital map (with spin-factor target $J\cong\R\oplus\R^m$,
domain $\ell_\infty^{2m}$ or $B(\C^{2m})_{\mathrm{sa}}$) that is at distance at
least $\sqrt\eps$ from \emph{every} positive unital map. Consequently an
approximate Jordan-isomorphism alone does not yield exact unital-positive factor
maps with the bridge exponent. The viable route is \emph{near-positive
projection stability}:
\[
  \begin{gathered}
  P\ \text{a }\delta\text{-positive unital idempotent},\quad \norm{P}\le1+\delta\\
  \Longrightarrow\
  \mathrm{dist}\bigl(P,\ \text{positive unital idempotents}\bigr)\le C\sqrt\delta,
  \end{gathered}
\]
which, if true, gives a genuine positive idempotent $E$ with
$\norm{E-P}=O(\sqrt\eta)$; \Cref{thm:effros-stormer} then applies to $E$ and
yields exact unital-positive factor maps through $J=E(\Bsa)$ with
$\norm{\Delta\Upsilon-\Phimap}=O(\sqrt\eta)$. This stability statement is
\status{(open)}: it is known classically only at the square-root scale (linear
stability is false), and the dimension-free case reduces to an unproved
stability theorem for almost-idempotent stochastic matrices.
\end{remark}

\subsection{Relation to van Luijk--Wilming}

The structures here are the approximate counterparts of an exact object from the
theory of quantum statistical experiments.

% PROV: vanLuijkWilming2026 paper.tex L1517-1524 (Theorem thm:luczak, eq:min-suff-J: J = intersection of Fix(T) over UP maps) and L235-247 (introthm:K-generates: J = Jstaralg(K), generated by Neyman-Pearson tests) -- the minimal sufficient J*-algebra is an intersection of fixed-point sets of UP maps, generated by Neyman-Pearson tests.
\begin{remark}[van Luijk--Wilming minimal sufficient Jordan algebra;
\status{(cited)}]\label{rem:vlw}
For a faithful statistical experiment $(\rho_\theta)$, the
\emph{minimal sufficient J*-algebra} is the J*-algebra
\[
  J_{(\rho_\theta)}=\bigcap\bigl\{\,\mathrm{Fix}(T)\ :\ T\text{ a }
  (\rho_\theta)\text{-preserving unital positive map on }L(\HH)\,\bigr\},
\]
an exact intersection of fixed-point sets of unital positive maps, and it ``is
generated by the Neyman--Pearson tests'' $[\rho>t\sigma]$
\cite{vanLuijkWilming2026}. Our near-fixed-point algebra $A=\Img P$ is the
\emph{approximate} analogue: $P$ replaces an exact conditional expectation onto
a fixed-point set by an approximate idempotent, and $a\bullet b=P(a\jp b)$
replaces the exact Effros--St\o rmer product
$r\bullet s=P(r\jp s)$ of \Cref{thm:effros-stormer}. In their setting the Jordan
algebra is always special (concretely realised, exceptional $H_3(\mathbb O)$
excluded); the bridge target inherits this, as recorded in \Cref{sec:programme}.
\end{remark}

\subsection{Status ledger}

\Cref{tab:status} summarises the standing of each component.

\begin{table}[ht]
\centering
\renewcommand{\arraystretch}{1.25}
\begin{tabular}{@{}p{0.42\linewidth}p{0.27\linewidth}p{0.21\linewidth}@{}}
\toprule
Component & Status & Where \\
\midrule
Layer-2 bridge (approx.\ Jordan algebra at $\sqrt\eta$)
  & proved, dimension-free
  & \Cref{sec:bridge} \\
Exponent $\eta$ (Kitaev strength)
  & UCP/cb: cited; decomposable: open
  & \Cref{rem:exponent} \\
Exact unital-positive factorization
  & open (needs projection stability)
  & \Cref{rem:rounding} \\
Layer-1 structure theorem
  & open (dimension-free homotopy)
  & \Cref{sec:programme} \\
Exceptional algebras ($H_3(\mathbb O)$)
  & channel target special; abstract layer open
  & \Cref{rem:vlw} \\
\bottomrule
\end{tabular}
\caption{Status of the components of the programme.}
\label{tab:status}
\end{table}

The two genuinely open problems are independent. The first is the
\emph{exponent}: whether decomposability (a dilation for each CP/co-CP summand)
restores the two-hole mechanism and upgrades $\sqrt\eta$ to $\eta$
(\Cref{rem:exponent}). The second is \emph{exact factorization}: whether a
near-positive idempotent is $O(\sqrt\eta)$-close to a genuine positive
idempotent, after which exact Effros--St\o rmer applies
(\Cref{rem:rounding}); generic positivity rounding is ruled out by the
spin-factor counterexample. The Layer-1 abstract structure theorem
(\Cref{sec:programme}) is open for a third, orthogonal reason: the
dimension-free bounded homotopy that Kitaev obtains from complete positivity has
no established Jordan analogue.
